# Persistent recovery gap in soil fungal communities after vegetation restoration: a meta-analysis

# Chapter I: Literature search

::: {style="background-color:#f0f0f0;"}
The literature search was carried out in the Web of Science Core Collection (<https://www.webofscience.com/>). Using the **Advanced Search** option, the following Boolean keyword combinations were applied to identify relevant studies. The retrieved literature was then manually sorted based on inclusion/exclusion criteria provided in Methods ("Literature search").

**First search**

TS=((Fungi) AND (restor\* OR "eco-restor\*" OR ecorestor\* OR revegetat\* OR "re-vegetat" OR plantation\* OR replant\* OR "re-plant\*" OR afforest\* OR reforest\* OR "re-forest" OR reclam\* OR "re-calm\*" OR rewild\* OR "re-wild\*" OR rehabilitat\* OR "re-habilitat\*" OR remediate\* OR recover\* OR reintroduc\* OR "re-introduc" OR abandon\* OR succession\*) AND (soil\* OR root\*) AND (diversity\* OR richness\* OR evenness\* OR relative abundan\* OR abundan\* OR composition\* OR community\* OR network\* OR biomass\* OR PLFA\* OR glomalin\* OR spore density\* OR colonization\* OR propagule\* OR hypha\* OR colony\* OR abundance\* OR phylogen\* OR gene copy\*) AND (ecolog\* OR environment\* OR ecosystem\*))

**Second search**

TS=((Fungi OR "soil fungi" OR microbe\* OR microorganism\* OR microbiome OR mycobiome OR mycobiota OR "fungal communit\*" OR "soil microfungi" OR "soil mycota") AND (restor\* OR "eco-restor" OR ecorestor OR revegetat\* OR "re-vegetat" OR plantation\* OR replant\* OR "re-plant" OR afforest OR reforest\* OR "re-forest" OR reclam\* OR "re-calm" OR rewild OR "re-wild" OR rehabilitat OR "re-habilitat" OR remediate OR recover\* OR reintroduc\* OR "re-introduc" OR abandon\* OR succession) AND (soil) AND (diversity OR richness\* OR evenness\* OR "relative abundan\*" OR abundan\* OR biomass\* OR PLFA) AND (NGS\* OR "high-throughput" OR metagenom\* OR amplicon\* OR "next-generation sequencing" OR Illumina OR MiSeq OR IonTorrent OR PacBio OR Nanopore OR 454 OR "ITS" OR "18S") AND (ecolog OR environment\* OR ecosystem\*))
:::

## PRISMA flowchart (Figure S1, Table S1)

```{r}
if (!requireNamespace("DiagrammeR", quietly = TRUE)) {
  install.packages("DiagrammeR")
}

library(DiagrammeR)
# Create PRISMA flowchart
Figure_S1 <- grViz("
digraph flowchart {

  graph [
    layout = dot,
    rankdir = TB,
    labelloc = t,
    label = 'Identification of studies via Web of Science core collection',
    fontname = Helvetica,
    fontsize = 12
  ]

  node [
    shape = box,
    style = filled,
    fillcolor = white,
    fontname = Helvetica,
    fontsize = 12
  ]

  edge [
    color = gray50,
    arrowsize = 1
  ]

  A1 [label = 'April 2024\\nRecords identified:\\n14,069']
  A2 [label = 'Records screened:\\n9,089']
  A3 [label = 'Records selected:\\n126']

  B1 [label = 'June 2025\\nRecords identified:\\n7,530']
  B2 [label = 'Records screened:\\n1,882']
  B3 [label = 'Records selected:\\n40']

  C [label = 'Records included:\\n166']

  A1 -> A2 -> A3
  B1 -> B2 -> B3

  A3 -> C
  B3 -> C
}
")
Figure_S1

```

# CHAPTER II: Data extraction

## Data extraction from tables

If reported, the relevant table was located, and the data were extracted.

### Data extraction from figures (boxplot, barplot etc.) (Table S2)

Before the extraction procedure, the figures available in the selected publication needed to be downloaded and saved. Here, an example figure was saved in the `Data_folder/example_shinyDigitise`.

#### Installation of shinyDigitise

The installation steps are available at this link <https://github.com/EIvimeyCook/ShinyDigitise> .

#### Load required package

```{r eval=FALSE}
library(shinyDigitise)
```

#### Run shinyDigitise

```{r eval = FALSE}
shinyDigitise("./Data_folder/example_shinyDigitise") #Use absolute path if this do not open floating window correctly
```

A floating window will be opened, and the subsequent steps should be followed.

For example, here is the example of figure.png loaded after clicking `GET EXTRACTING`.

The following steps have to be followed: **Orientate Figure → Calibrate Axes → Extract Data**. Upon completion, a message will be displayed in the R console.

## Data extraction from ordination plots (Table S3)

#### Open figure in Datathief

This step was performed outside the R environment. The **Datathief.jar** file was opened, which launched a window as shown below:

#### Manual extraction of coordinates

The ordination plot saved in the folder was opened. The axes were then calibrated by moving the "brown," "blue," and "green" points and entering the corresponding x-axis and y-axis coordinates for all three points. To obtain the coordinates of each individual point in the plot, each moving point was adjusted to the respective location, and the coordinates were recorded manually. These coordinates are provided in Supplementary Table S3 under the **Axis1** and **Axis2** columns.

#### Calculation of euclidean distance

##### Data preparation

The data should consist of three columns: **Plot**, **Axis1**, and **Axis2**, containing the coordinates of each point. For example, as provided in `Data_folder/example_DataThief/ordination_point.csv`, the `df` dataset should appear as follows:

Smilarly plot category data `Data_folder/example_DataThief/ordination_point_category.csv` should look like:

##### Calculation step

```{r eval=FALSE}
# Import df data
df<- read.csv(file = "Data_folder/example_DataThief/ordination_point.csv", header = TRUE, row.names = 1)

# Calculate Euclidean distance matrix
dist_mat<- vegdist(df, method = "euclidean")
dist_matrix<- as.matrix(dist_mat)

# Copy plot category table from excel sheet
# Read group plot category from clipboard
comparison<- read.csv(file = "Data_folder/example_DataThief/ordination_point_category.csv", header = TRUE, row.names = 1)

# Get unique comparison types
comparison_types <- unique(unlist(comparison))

# Calculate WITHIN-group distances
within_distances <- list()
for (type in comparison_types) {
  samples<- rownames(comparison)[comparison[, 1] == type]
  if (length(samples) > 1) {
    sub_dist <- dist_matrix[samples, samples]
    within_distances[[type]] <- sub_dist[upper.tri(sub_dist)]  # Get upper triangle (no duplicates)
  }
}

# Calculate mean and SD for within-group distances
mean_within <- sapply(within_distances, mean)
sd_within   <- sapply(within_distances, sd)

# Calculate BETWEEN-group distances
type_pairs <- combn(comparison_types, 2, simplify = FALSE)  # All possible pairs
between_distances <- list()
for (pair in type_pairs) {
  type1   <- pair[1]
  type2   <- pair[2]
  samples1 <- rownames(comparison)[comparison[, 1] == type1]
  samples2 <- rownames(comparison)[comparison[, 1] == type2]
  between_distances[[paste(type1, type2, sep = "_vs_")]] <-
    as.vector(dist_matrix[samples1, samples2])  # All distances between groups
}

# Calculate mean and SD for between-group distances
mean_between <- sapply(between_distances, mean)
sd_between   <- sapply(between_distances, sd) 

# Compile results
result <- list(
  mean_within_groups = mean_within,
  sd_within_groups   = sd_within,
  mean_between_groups = mean_between,
  sd_between_groups   = sd_between
)
result
```

From the results displayed in the R console, the relevant data were copied. These data are presented in Supplementary Table S3.

# CHAPTER III: Data overview

## Install and load required packages

```{r message = FALSE, warning = FALSE}
packages <- c("metafor","numDeriv","metadat","Matrix","gridExtra",  "dplyr","forcats","sf","maps","ggplot2",  "gtable","crayon","tidyselect","Rcpp","dichromat",  "systemfonts","scales","textshaping","lattice","R6",  "labeling","generics","classInt","tibble","units",  "DBI","pillar","RColorBrewer","rlang","utf8",  "mathjaxr","S7","cli","withr","magrittr","class",  "digest","nlme","lifecycle","vctrs","KernSmooth",  "proxy","glue","farver","ragg","e1071","pkgconfig",  "vegan","ggpubr","patchwork","cowplot", "grid")

# cache installed packages
installed <- rownames(installed.packages())
to_install <- setdiff(packages, installed)

if (length(to_install) > 0) {
  install.packages(to_install, dependencies = TRUE)
}

# load packages safely
invisible(lapply(packages, function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    stop(paste("Failed to load package:", pkg))
  }
}))
```

## Study distribution map

```{r}
distribution <- read.csv("data/data_overview/distribution.csv", header = TRUE)

# LOAD WORLD MAP
world_map <- map_data("world")

# BASE MAP
base_world_with_grid <- ggplot() + geom_polygon(data = world_map, aes(x = long, y = lat, group = group), fill = "lightblue", color = "transparent") + coord_quickmap(xlim = c(-160, 175), ylim = c(-55, 80)) + theme_bw() + theme(panel.grid = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.border = element_blank()) + labs(x = NULL, y = NULL)

# FACTOR ORDERING
distribution$Ecosystem <- factor(distribution$Ecosystem, levels = c("Forest", "Grassland"))

distribution$Prior_land_use <- factor(distribution$Prior_land_use, levels = c("Agriculture", "Pasture", "Mining", "Deforestation", "Erosion", "Monoculture plantation", "Others"))
```

## Figure 1

```{r}
# FINAL MAP
figure_1 <- base_world_with_grid + geom_point(data = distribution, aes(x = Longitude, y = Latitude, fill = Prior_land_use, shape = Ecosystem), size = 1, alpha = 0.5, color = "black", stroke = 0.3) + scale_fill_manual(values = c("Agriculture" = "red", "Pasture" = "blue", "Mining" = "darkgreen", "Deforestation" = "orange", "Erosion" = "brown", "Monoculture plantation" = "cyan", "Others" = "yellow")) + scale_shape_manual(values = c("Grassland" = 21, "Forest" = 22)) + labs(fill = "Prior land use", shape = "Ecosystem") + theme(legend.title = element_text(size = 10), legend.text = element_text(size = 8), legend.position = "right", strip.background = element_blank()) + facet_wrap(~Restoration_strategy, nrow = 2) + guides(shape = guide_legend(order = 1, override.aes = list(fill = "black", color = "black", size = 2.5), keyheight = unit(0.3, "cm"), keywidth = unit(0.8, "cm")), fill = guide_legend(order = 2, override.aes = list(shape = 21, color = "black", size = 2.5), keyheight = unit(0.3, "cm"), keywidth = unit(0.8, "cm")))
figure_1
```

```{r eval=FALSE}
ggsave("../Figure_1.tiff", plot = figure_1, dpi = 600, height = 7, width = 7)
```

## Data overview

```{r}
data_overview <- read.csv("data/data_overview/data_overview.csv", header =TRUE)
# ECOSYSTEM TYPE
df_ecosystem <- data_overview[1:2,]
df_restoration <- data_overview[3:4,]
df_prior_land_use <- data_overview[5:11,]

ecosystem_overview_plot <- ggplot(df_ecosystem, aes(x = Types, y = n, fill = Types)) + geom_col(width = 0.6, alpha = 0.6) + geom_text(aes(label = n), hjust = -0.2, size = 3) + scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + scale_y_continuous(expand = expansion(mult = c(0, 0.25))) + coord_flip(clip = "off") + labs(title = "Ecosystem", x = NULL, y = "Number of studies") + theme_classic(base_size = 10) + theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10, face = "bold"), axis.line = element_line(color = "black"))
ecosystem_overview_plot

df_prior_land_use$Types <- factor(df_prior_land_use$Types, levels = df_prior_land_use$Types[order(df_prior_land_use$n, decreasing = TRUE)])
disturbance_overview_plot <- ggplot(df_prior_land_use, aes(x = Types, y = n)) + geom_col(width = 0.6, alpha = 0.6, fill = "grey50") + geom_text(aes(label = n), hjust = -0.2, size = 3) + scale_y_continuous(expand = expansion(mult = c(0, 0.25))) + coord_flip(clip = "off") + labs(title = "Prior land use", x = NULL, y = "Number of studies") + theme_classic(base_size = 10) + theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10, face = "bold"), axis.line = element_line(color = "black"))
disturbance_overview_plot

strategy_overview_plot <- ggplot(df_restoration, aes(x = Types, y = n, fill = Types)) + geom_col(width = 0.6, alpha = 0.6) + geom_text(aes(label = n), hjust = -0.2, size = 3) + scale_fill_manual(values = c("Active restoration" = "maroon", "Natural regeneration" = "darkgreen")) + scale_y_continuous(expand = expansion(mult = c(0, 0.25))) + coord_flip(clip = "off") + labs(title = "Restoration strategy", x = NULL, y = "Number of studies") + theme_classic(base_size = 10) + theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10, face = "bold"), axis.line = element_line(color = "black"))
strategy_overview_plot

# RESTORATION TIME
restoration_time <- read.csv("data/data_overview/restoration_time.csv", header = TRUE)
restoration_time <- restoration_time %>% mutate(Restoration_strategy = recode(Restoration_strategy, "Active" = "Active restoration", "Passive" = "Natural regeneration"))
median(restoration_time$Restoration_time)

restoration_time %>%group_by(Restoration_strategy) %>%  summarise(mean_restoration_time = median(Restoration_time, na.rm = TRUE))
restoration_time_all <- restoration_time %>%  bind_rows(restoration_time %>% mutate(Restoration_strategy = "Overall")) %>%  mutate(Restoration_strategy = factor(Restoration_strategy, levels = c("Overall", "Active restoration","Natural regeneration")))

time_boxplot <- restoration_time_all %>% ggplot(aes(x = Restoration_strategy, y = Restoration_time, fill = Restoration_strategy)) + geom_boxplot(outlier.shape = NA, alpha = 0.6) + geom_jitter(aes(color = Restoration_strategy), width = 0.1, size = 1.5, alpha = 0.6, shape = 16, stroke = 0.3) + scale_fill_manual(values = c("Active restoration" = "maroon", "Natural regeneration" = "darkgreen", "Overall" = "gray40")) + scale_color_manual(values = c("Active restoration" = "maroon", "Natural regeneration" = "darkgreen", "Overall" = "gray40")) + scale_y_continuous(breaks = seq(0, max(restoration_time$Restoration_time, na.rm = TRUE), by = 20)) + labs(x = NULL, y = "Restoration time (years)", title = "Restoration time") + coord_flip() + theme_classic(base_size = 10) + theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10, face = "bold"))
time_boxplot
```

## Figure 2

```{r}
# COMBINE PLOTS
figure_2 <- plot_grid(ecosystem_overview_plot, disturbance_overview_plot, strategy_overview_plot, time_boxplot, ncol = 2, nrow = 2, labels = c("(a)", "(b)", "(c)", "(d)"), label_size = 11, label_x = 0.98, label_y = 0.98, hjust = 1, vjust = 1, align = "hv", axis = "tblr", rel_widths = c(1, 1.2))
figure_2
```

```{r eval=FALSE}
ggsave("../Figure_2.tiff", plot = figure_2, dpi = 600, height = 5, width = 6)
```

## Data overview by metrics

```{r warning=FALSE}
# ECOSYSTEM TYPE
ecosystem_summary <- read.csv("data/data_overview/ecosystem_summary.csv", header = TRUE)

# ECOSYSTEM TYPE
data_segmented_ecosystem <- ecosystem_summary %>% mutate( Metrics = factor(Metrics, levels = c("OTU richness","Chao1 richness", "Shannon index", "Simpson index", "Ascomycota","Basidiomycota", "Beta diversity", "Structure", "PLFA content")),Ecosystem = factor(Ecosystem, levels = c("Forest","Grassland")))

break_threshold <- 50
data_segmented_ecosystem <- data_segmented_ecosystem %>%  mutate(needs_break = Comparison > break_threshold, segment_end = ifelse(needs_break, break_threshold * 0.9, Comparison))
spacing_multiplier <- 3
data_segmented_ecosystem <- data_segmented_ecosystem %>% mutate(x_position = (as.numeric(Metrics) - 1) * spacing_multiplier + 1)

min_x <- min(data_segmented_ecosystem$x_position) - 1
max_x <- max(data_segmented_ecosystem$x_position) + 1
center_x <- (min_x + max_x) / 2 

overview_ecosystem <- ggplot(data_segmented_ecosystem, aes(x = center_x, y = 0)) + geom_segment(aes(xend = x_position, yend = segment_end, color = Metrics), linewidth = 1, lineend = "round") + geom_segment(data = subset(data_segmented_ecosystem, needs_break == TRUE), aes(x = x_position, xend = x_position, y = break_threshold * 1.1, yend = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3, color = Metrics), linewidth = 1, lineend = "round") + geom_hline(yintercept = 0, color = "black", size = 0.2) + geom_point(data = subset(data_segmented_ecosystem, needs_break == TRUE), aes(x = x_position, y = break_threshold), shape = 21, fill = "white", color = "transparent", size = 2) + geom_text(data = subset(data_segmented_ecosystem, needs_break == TRUE), aes(x = x_position, y = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3, label = Comparison), vjust = -0.8, size = 2.5) + geom_text(data = subset(data_segmented_ecosystem, !needs_break), aes(x = x_position, y = Comparison, label = Comparison), vjust = -0.8, size = 2.5) + facet_wrap(~Ecosystem, nrow = 1, strip.position = "bottom") + labs(x = NULL, y = NULL, title = "Ecosystem") + scale_color_manual(values = c("OTU richness" = "darkgreen", "Chao1 richness" = "limegreen", "Shannon index" = "springgreen", "Simpson index" = "cyan3", "Ascomycota" = "orange", "Basidiomycota" = "brown", "Beta diversity" = "blue", "Structure" = "steelblue", "PLFA content" = "grey60")) + theme_bw() + theme(legend.position = "none", axis.text = element_blank(), axis.ticks = element_blank(), axis.line = element_blank(), plot.title = element_text(size = 10, hjust = 0.5, face = "bold"), panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(), strip.text = element_text(color = "black", face = "plain"), panel.spacing.x = unit(0.5, "cm")) + coord_cartesian(xlim = c(min_x, max_x), ylim = c(0, max(data_segmented_ecosystem$Comparison) * 0.5), clip = "off")
```

```{r}
# RESTORATION STRATEGY
restoration_strategy_summary <- read.csv("data/data_overview/restoration_strategy_summary.csv", header = TRUE)

# RESTORATION STRATEGY
restoration_metrics_summary <- restoration_strategy_summary %>% mutate(Restoration_strategy = recode(Restoration_strategy, "Active" = "Active restoration", "Passive" = "Natural regeneration"))

data_segmented_restoration <- restoration_metrics_summary %>% rename(Restoration_activity = Restoration_strategy) %>%  mutate(Metrics = factor(Metrics, levels = c("OTU richness","Chao1 richness", "Shannon index", "Simpson index",  "Ascomycota","Basidiomycota", "Beta diversity", "Structure", "PLFA content")),  Restoration_activity = factor(Restoration_activity, levels = c("Active restoration", "Natural regeneration")))
break_threshold <- 50

data_segmented_restoration <- data_segmented_restoration %>%  mutate( needs_break = Comparison > break_threshold, segment_end = ifelse(needs_break, break_threshold * 0.9, Comparison))

spacing_multiplier <- 3
data_segmented_restoration <- data_segmented_restoration %>% mutate(x_position = (as.numeric(Metrics) - 1) * spacing_multiplier + 1)

min_x <- min(data_segmented_restoration$x_position) - 1
max_x <- max(data_segmented_restoration$x_position) + 1
center_x <- (min_x + max_x) / 2 

overview_restoration <- ggplot(data_segmented_restoration, aes(x = center_x, y = 0)) + geom_segment(aes(xend = x_position, yend = segment_end, color = Metrics), linewidth = 1, lineend = "round") + geom_segment(data = subset(data_segmented_restoration, needs_break == TRUE), aes(x = x_position, xend = x_position, y = break_threshold * 1.1, yend = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3, color = Metrics), linewidth = 1, lineend = "round") + geom_hline(yintercept = 0, color = "black", size = 0.2) + geom_point(data = subset(data_segmented_restoration, needs_break == TRUE), aes(x = x_position, y = break_threshold), shape = 21, fill = "white", color = "transparent", size = 2) + geom_text(data = subset(data_segmented_restoration, needs_break == TRUE), aes(x = x_position, y = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3, label = Comparison), vjust = -0.8, size = 2.5) + geom_text(data = subset(data_segmented_restoration, !needs_break), aes(x = x_position, y = Comparison, label = Comparison), vjust = -0.8, size = 2.5) + facet_wrap(~Restoration_activity, nrow = 1, strip.position = "bottom") + labs(x = NULL, y = NULL, title = "Restoration strategy") + scale_color_manual(values = c("OTU richness" = "darkgreen", "Chao1 richness" = "limegreen", "Shannon index" = "springgreen", "Simpson index" = "cyan3", "Ascomycota" = "orange", "Basidiomycota" = "brown", "Beta diversity" = "blue", "Structure" = "steelblue", "PLFA content" = "grey60")) + theme_bw() + theme(legend.position = "none", axis.text = element_blank(), axis.ticks = element_blank(), axis.line = element_blank(), plot.title = element_text(size = 10, hjust = 0.5, face = "bold"), panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(), strip.text = element_text(color = "black", face = "plain"), panel.spacing.x = unit(0.5, "cm")) + coord_cartesian(xlim = c(min_x, max_x), ylim = c(0, max(data_segmented_restoration$Comparison) * 0.5), clip = "off")
```

```{r}
# PRIOR LAND USE
prior_land_use_summary <- read.csv("data/data_overview/prior_land_use_summary.csv", header = TRUE)

# PRIOR LAND USE
prior_land_use_summary$Metrics <- factor(prior_land_use_summary$Metrics, levels = c("OTU richness", "Chao1 richness","Shannon index", "Simpson index", "Ascomycota", "Basidiomycota","Beta diversity", "Structure", "PLFA content"))

prior_land_use_summary$Prior_land_use <- factor(prior_land_use_summary$Prior_land_use, levels = c("Agriculture", "Deforestation", "Erosion", "Mining", "Monoculture plantation", "Pasture","Others"))

break_threshold <- 50
data_segmented_Prior_land_use <- prior_land_use_summary %>% mutate(needs_break = Comparison > break_threshold, segment_end = ifelse(needs_break, break_threshold * 0.9, Comparison))

max_metrics <- max(as.numeric(factor(data_segmented_Prior_land_use$Metrics)))
spacing_multiplier <- 3

data_segmented_Prior_land_use <- data_segmented_Prior_land_use %>% mutate(x_position = (as.numeric(factor(Metrics)) - 1) * spacing_multiplier + 1)

min_x <- min(data_segmented_Prior_land_use$x_position) - 1
max_x <- max(data_segmented_Prior_land_use$x_position) + 1
center_x <- (min_x + max_x) / 2 

# PLOT
overview_Prior_land_use <- ggplot(data_segmented_Prior_land_use, aes(x = center_x, y = 0)) + geom_segment(aes(xend = x_position, yend = segment_end, color = Metrics), size = 1, lineend = "round") + geom_segment(data = subset(data_segmented_Prior_land_use, needs_break == TRUE), aes(x = x_position, xend = x_position, y = break_threshold * 1.1, yend = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3, color = Metrics), size = 1, lineend = "round") + geom_hline(yintercept = 0, color = "black", size = 0.2) + geom_point(data = subset(data_segmented_Prior_land_use, needs_break == TRUE), aes(x = x_position, y = break_threshold), shape = 21, fill = "white", color = "transparent", size = 2) + geom_text(data = subset(data_segmented_Prior_land_use, needs_break == TRUE), aes(x = x_position, y = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3, label = Comparison), vjust = -0.8, size = 2.5) + geom_text(data = subset(data_segmented_Prior_land_use, !needs_break), aes(x = x_position, y = Comparison, label = Comparison), vjust = -0.8, size = 2.5) + facet_wrap(~Prior_land_use, nrow = 1, strip.position = "bottom") + labs(x = NULL, y = NULL, color = NULL, title = "Prior land use") + scale_color_manual(values = c("OTU richness" = "darkgreen", "Chao1 richness" = "limegreen", "Shannon index" = "springgreen", "Simpson index" = "cyan3", "Ascomycota" = "orange", "Basidiomycota" = "brown", "Beta diversity" = "blue", "Structure" = "steelblue", "PLFA content" = "grey60")) + theme_bw() + theme(legend.position = "bottom", legend.text = element_text(size = 8), axis.text = element_blank(), axis.ticks = element_blank(), axis.line = element_blank(), plot.title = element_text(size = 10, hjust = 0.5, face = "bold"), panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(), strip.text = element_text(color = "black"), panel.spacing.x = unit(0.2, "cm"), panel.spacing.y = unit(-0.5, "cm"), plot.margin = margin(0, 0, 0, 0, "pt")) + coord_cartesian(xlim = c(min_x, max_x), ylim = c(0, max(data_segmented_Prior_land_use$Comparison) * 0.7), clip = "off")
```

## Figure S2

```{r}
top_row <- plot_grid( overview_ecosystem, overview_restoration, ncol = 2, labels = c("(a)", "(b)"), label_size = 12, label_x = 0.98, label_y = 0.98,  hjust = 1, align = 'h',  axis = 'bt' )
Figure_S2 <- plot_grid(top_row, overview_Prior_land_use,  ncol = 1, labels = c("", "(c)"), label_size = 12,label_x = 0.98, label_y = 0.98, hjust = 1, rel_heights = c(1, 1.8), align = 'v', axis = 'lr')
Figure_S2
```

```{r eval=FALSE}
ggsave("../Figure_S2.tiff", plot = Figure_S2, dpi = 600, height = 7, width = 7)
```

# Chapter VI: Publication bias

## Restored vs Degraded

### Load data

```{r}
# FUNCTION TO LOAD DATA (RESTORED VS DEGRADED)
load_data_deg <- function(file_path) {read.csv(file_path, header = TRUE) %>%mutate(across(c(ID, Restoration_strategy, Ecosystem, Prior_land_use), as.factor), Restoration_time = as.numeric(Restoration_time), ControlID = paste(ID, Degraded_Mean, Degraded_SD, Degraded_SS, sep = "_")) %>%   mutate(ControlID = as.character(ControlID))}

# RESTORED VS DEGRADED DATA
## ALPHA DIVERSITY
otu_resvsdeg_df      <- load_data_deg("data/original_data/otu_resvsdeg.csv")
chao1_resvsdeg_df    <- load_data_deg("data/original_data/chao1_resvsdeg.csv")
shannon_resvsdeg_df  <- load_data_deg("data/original_data/shannon_resvsdeg.csv")
simpson_resvsdeg_df  <- load_data_deg("data/original_data/simpson_resvsdeg.csv")

## RELATIVE ABUNDANCE
asco_resvsdeg_df     <- load_data_deg("data/original_data/asco_resvsdeg.csv")
basidio_resvsdeg_df  <- load_data_deg("data/original_data/basidio_resvsdeg.csv")

## COMPOSITION
beta_resvsdeg_df     <- load_data_deg("data/original_data/beta_resvsdeg.csv")
comp_resvsdeg_df     <- load_data_deg("data/original_data/comp_resvsdeg.csv")

## BIOMASS
plfa_resvsdeg_df     <- load_data_deg("data/original_data/PLFA_resvsdeg.csv")
```

### Response ratio

```{r}
# FUNCTION TO CALCULATE RESPONSE RATIO
compute_rr_deg <- function(df) {metafor::escalc(measure = "ROM", n1i = Restored_SS,  n2i = Degraded_SS, m1i = Restored_Mean,  m2i = Degraded_Mean, sd1i = Restored_SD,  sd2i = Degraded_SD, data = df )}

# RESPONSE RATIO (RESTORED VS DEGRADED)
## ALPHA DIVERSITY
otu_resvsdeg_df     <- compute_rr_deg(otu_resvsdeg_df)
chao1_resvsdeg_df   <- compute_rr_deg(chao1_resvsdeg_df)
shannon_resvsdeg_df <- compute_rr_deg(shannon_resvsdeg_df)
simpson_resvsdeg_df <- compute_rr_deg(simpson_resvsdeg_df)

## RELATIVE ABUNDANCE
asco_resvsdeg_df <- compute_rr_deg(asco_resvsdeg_df)
basidio_resvsdeg_df <- compute_rr_deg(basidio_resvsdeg_df)

## COMPOSITION
beta_resvsdeg_df <- compute_rr_deg(beta_resvsdeg_df)
comp_resvsdeg_df <- comp_resvsdeg_df # DATA ALREADY CONTAIN ln(RR)

## BIOMASS
plfa_resvsdeg_df <- compute_rr_deg(plfa_resvsdeg_df)
```

### Figure S3.1

```{r}
#| fig-width: 6
#| fig-height: 8
#| dpi: 600

par(mfrow = c(3, 3), mar = c(4, 4, 3, 1), mgp = c(3, 1, 0))

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = otu_resvsdeg_df),
       main = "OTU richness", xlab = "lnRR", ylab = "SE")

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = chao1_resvsdeg_df),
       main = "Chao1 richness", xlab = "lnRR", ylab = NA)

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = shannon_resvsdeg_df),
       main = "Shannon index", xlab = "lnRR", ylab = NA)

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = simpson_resvsdeg_df),
       main = "Simpson index", xlab = "lnRR", ylab = NA)

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = asco_resvsdeg_df),
       main = "Ascomycota", xlab = "lnRR", ylab = "SE")

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = basidio_resvsdeg_df),
       main = "Basidiomycota", xlab = "lnRR", ylab = NA)

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = beta_resvsdeg_df),
       main = "Beta diversity", xlab = "lnRR", ylab = "SE")

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = comp_resvsdeg_df),
       main = "Structure", xlab = "lnRR", ylab = "SE")

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = plfa_resvsdeg_df),
       main = "PLFA content", xlab = "lnRR", ylab = NA)
```

### Egger's test (Table S4.1)

```{r}
egger <- function(df) { model <- metafor::rma(yi = yi, vi = vi, data = df, method = "REML"); test <- metafor::regtest(model); p <- test$pval; sig <- ifelse(p < 0.001, "***", ifelse(p < 0.01, "**", ifelse(p < 0.05, "*", ifelse(p < 0.1, ".", "")))); data.frame(Z = round(test$zval, 3), p = format(round(p, 3), nsmall = 3), Sig = sig) }

egger_results_deg <- rbind(data.frame(Metrics = "OTU (restored vs degraded)",egger(otu_resvsdeg_df)),  data.frame(Metrics = "Chao1 (restored vs degraded)",egger(chao1_resvsdeg_df)),  data.frame(Metrics = "Shannon (restored vs degraded)",egger(shannon_resvsdeg_df)),  data.frame(Metrics = "Simpson (restored vs degraded)",egger(simpson_resvsdeg_df)),  data.frame(Metrics = "Asco (restored vs degraded)", egger(asco_resvsdeg_df)),  data.frame(Metrics = "Basidio (restored vs degraded)",egger(basidio_resvsdeg_df)),  data.frame(Metrics = "Beta (restored vs degraded)", egger(beta_resvsdeg_df)),  data.frame(Metrics = "Structure (restored vs degraded)", egger(comp_resvsdeg_df)),  data.frame(Metrics = "PLFA (restored vs degraded)",egger(plfa_resvsdeg_df)))
print(egger_results_deg)

```

## Restored vs Reference

### Load data

```{r}
# FUNCTION TO LOAD DATA (RESTORED VS REFERENCE)
load_data_ref <- function(file_path) {read.csv(file_path, header = TRUE) %>%    mutate(across(c(ID, Restoration_strategy, Ecosystem, Prior_land_use), as.factor), Restoration_time = as.numeric(Restoration_time),
      ControlID = paste(ID, Reference_Mean, Reference_SD, Reference_SS, sep = "_")) %>% mutate(ControlID = as.character(ControlID))}

# RESTORED VS REFERENCE DATA
## ALPHA DIVERSITY
otu_resvsref_df     <- load_data_ref("data/original_data/otu_resvsref.csv")
chao1_resvsref_df   <- load_data_ref("data/original_data/chao1_resvsref.csv")
shannon_resvsref_df <- load_data_ref("data/original_data/shannon_resvsref.csv")
simpson_resvsref_df <- load_data_ref("data/original_data/simpson_resvsref.csv")

## RELATIVE ABUNDANCE
asco_resvsref_df    <- load_data_ref("data/original_data/asco_resvsref.csv")
basidio_resvsref_df <- load_data_ref("data/original_data/basidio_resvsref.csv")

## COMPOSITION
beta_resvsref_df    <- load_data_ref("data/original_data/beta_resvsref.csv")
comp_resvsref_df    <- load_data_ref("data/original_data/comp_resvsref.csv")

## BIOMASS
plfa_resvsref_df    <- load_data_ref("data/original_data/plfa_resvsref.csv")

```

### Response ratio

```{r}
#FUNCTION TO CALCULATE RESPONSE RATIO (RESTORED VS REFERENCE)
compute_rr_ref <- function(df) {metafor::escalc(measure = "ROM",  n1i = Restored_SS,    n2i = Reference_SS, m1i = Restored_Mean,  m2i = Reference_Mean, sd1i = Restored_SD,   sd2i = Reference_SD,  data = df )}

#RESPONSE RATIO (RESTORED VS REFERENCE)
##ALPHA DIVERSITY
otu_resvsref_df     <- compute_rr_ref(otu_resvsref_df)
chao1_resvsref_df   <- compute_rr_ref(chao1_resvsref_df)
shannon_resvsref_df <- compute_rr_ref(shannon_resvsref_df)
simpson_resvsref_df <- compute_rr_ref(simpson_resvsref_df)

##RELATIVE ABUNDANCE
asco_resvsref_df    <- compute_rr_ref(asco_resvsref_df)
basidio_resvsref_df <- compute_rr_ref(basidio_resvsref_df)

##COMPOSITION
beta_resvsref_df    <- compute_rr_ref(beta_resvsref_df)
comp_resvsref_df <- comp_resvsref_df # DATA ALREADY CONTAIN ln(RR)

## BIOMASS
plfa_resvsref_df    <- compute_rr_ref(plfa_resvsref_df)
```

### Figure S3.2

```{r}
#| fig-width: 6
#| fig-height: 8
#| dpi: 600

par(mfrow = c(3, 3), mar = c(4, 4, 3, 1), mgp = c(3, 1, 0))

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = otu_resvsref_df),
       main = "OTU richness", xlab = "lnRR", ylab = "SE")

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = chao1_resvsref_df),
       main = "Chao1 richness", xlab = "lnRR", ylab = NA)

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = shannon_resvsref_df),
       main = "Shannon index", xlab = "lnRR", ylab = NA)

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = simpson_resvsref_df),
       main = "Simpson index", xlab = "lnRR", ylab = NA)

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = asco_resvsref_df),
       main = "Ascomycota", xlab = "lnRR", ylab = "SE")

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = basidio_resvsref_df),
       main = "Basidiomycota", xlab = "lnRR", ylab = NA)

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = beta_resvsref_df),
       main = "Beta diversity", xlab = "lnRR", ylab = "SE")

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = comp_resvsref_df),
       main = "Structure", xlab = "lnRR", ylab = "SE")

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = plfa_resvsref_df),
       main = "PLFA content", xlab = "lnRR", ylab = NA)
```

### Egger's test (Table S4.2)

```{r}
egger_results_ref <- rbind( data.frame(Metrics = "OTU (restored vs reference)",egger(otu_resvsref_df)),  data.frame(Metrics = "Chao1 (restored vs reference)",egger(chao1_resvsref_df)),  data.frame(Metrics ="Shannon (restored vs reference)",egger(shannon_resvsref_df)),  data.frame(Metrics ="Simpson (restored vs reference)",egger(simpson_resvsref_df)),  data.frame(Metrics = "Asco (restored vs reference)", egger(asco_resvsref_df)),  data.frame(Metrics ="Basidio (restored vs reference)",egger(basidio_resvsref_df)),  data.frame(Metrics = "Beta (restored vs reference)", egger(beta_resvsref_df)),  data.frame(Metrics ="Structure (restored vs reference)", egger(comp_resvsref_df)),  data.frame(Metrics ="PLFA (restored vs reference)",egger(plfa_resvsref_df)))
print(egger_results_ref)
```

# Chapter VII: Overall restoration effect

```{r}
# CONSTRUCTING VARIANCE-COVARIANCE MATRIX
build_cov_matrix <- function(df, rho) { V <- matrix(0, nrow(df), nrow(df)); for (g in split(seq_len(nrow(df)), df$ControlID)) { sub <- df[g, ]; k <- length(g); if (k == 1) { V[g, g] <- sub$vi } else { Vb <- rho * sqrt(outer(sub$vi, sub$vi)); diag(Vb) <- sub$vi; V[g, g] <- Vb } }; diag(V) <- diag(V) + 1e-8; V }


# SENSITIVITY ANALYSIS FOR CORRELATION AMONG MULTIPLE EFFECT SIZES
run_sensitivity <- function(df, rho_vals = c(0.2, 0.5, 0.8)) { models <- lapply(rho_vals, function(rho) { rma.mv(yi = df$yi, V = build_cov_matrix(df, rho = rho), random = ~ 1 | ID, method = "REML", data = df) }); extract_results <- function(mod, rho) { s <- summary(mod); data.frame(rho = rho, estimate = s$beta[1], ci.lb = s$ci.lb[1], ci.ub = s$ci.ub[1], pval = s$pval[1]) }; do.call(rbind, Map(extract_results, models, rho_vals)) }

run_sensitivity_2 <- function(df, rho_vals = c(0.2, 0.5, 0.8)) { models <- lapply(rho_vals, function(rho) { rma.mv(yi = df$yi, V = build_cov_matrix(df, rho = rho), random = ~ 1 | ID, method = "REML", control = list(optimizer = "optim", maxit = 10000), data = df) }); extract_results <- function(mod, rho) { s <- summary(mod); data.frame(rho = rho, estimate = s$beta[1], ci.lb = s$ci.lb[1], ci.ub = s$ci.ub[1], pval = s$pval[1]) }; do.call(rbind, Map(extract_results, models, rho_vals)) }

# EXTRACT TEST OF HETEROGENEITY
get_heterogeneity <- function(mod) { s <- summary(mod); data.frame(QE = s$QE, QE_df = s$QEdf, QE_p = s$QEp, tau2 = s$sigma2, tau = sqrt(s$sigma2)) }


# FIND OUTLIERS AND REMOVE IF ANY
get_outliers <- function(model, data, z_thresh = 3) { res_stud <- rstudent(model); cd_vals <- cooks.distance(model); outlier_idx <- intersect(which(abs(res_stud$z) > z_thresh), which(cd_vals > (4 / nrow(data)))); outlier_idx }

remove_outliers <- function(df, outlier_idx) { if (length(outlier_idx) > 0) { message("Removing influential outliers for ", paste(outlier_idx, collapse = ", ")); return(df[-outlier_idx, ]) } else { return(df) } }

get_results <- function(mod, data, label) { s <- summary(mod); int_pos <- which(rownames(s$beta) == "intrcpt"); strategy_k <- sum(data$Restoration_strategy == label, na.rm = TRUE); data.frame(Restoration_strategy = label, K = strategy_k, Estimate = round(s$beta[int_pos, ], 3), ci.lb = round(s$ci.lb[int_pos], 3), ci.ub = round(s$ci.ub[int_pos], 3), pval = s$pval[int_pos], Percentage = round((exp(s$beta[int_pos, ]) - 1) * 100, 1), Perc_lb = round((exp(s$ci.lb[int_pos]) - 1) * 100, 1), Perc_ub = round((exp(s$ci.ub[int_pos]) - 1) * 100, 1), Significance = ifelse(s$pval[int_pos] < 0.05, "*", "")) }


get_results_prior_land_use <- function(mod, data, label) { s <- summary(mod); int_pos <- which(rownames(s$beta) == "intrcpt"); land_k <- sum(tolower(trimws(as.character(data$Prior_land_use))) == tolower(trimws(label)), na.rm = TRUE); data.frame(Prior_land_use = label, K = paste0("(", land_k, ")"), Estimate = round(s$beta[int_pos, ], 3), ci.lb = round(s$ci.lb[int_pos], 3), ci.ub = round(s$ci.ub[int_pos], 3), pval = s$pval[int_pos], Percentage = paste0(round((exp(s$beta[int_pos, ]) - 1) * 100, 1), "%"), Perc_lb = paste0(round((exp(s$ci.lb[int_pos]) - 1) * 100, 1), "%"), Perc_ub = paste0(round((exp(s$ci.ub[int_pos]) - 1) * 100, 1), "%"), Significance = ifelse(s$pval[int_pos] < 0.05, "*", "")) }

# EXTRACT SUMMARY STATISTICS
extract_meta_result <- function(res, metric, ecosystem) { data.frame(Metric = metric, Ecosystem = ecosystem, k = res$k, lnRR = round(as.numeric(res$beta), 3), SE = round(res$se, 3), ci.lb = round(res$ci.lb, 3), ci.ub = round(res$ci.ub, 3), pval = round(res$pval, 4), Percent_Change = round((exp(as.numeric(res$beta)) - 1) * 100, 1)) }

report_table <- function(res_list, metric_name) { do.call(rbind, lapply(names(res_list), function(ecos) { extract_meta_result(res = res_list[[ecos]], metric = metric_name, ecosystem = ecos) })) }

get_coefficient <- function(model) { coefs <- coef(summary(model)); beta_forest <- coefs["log_time", "estimate"]; beta_grass <- beta_forest + coefs["log_time:EcosystemGrassland", "estimate"]; p_forest <- coefs["log_time", "pval"]; p_grass <- coefs["log_time:EcosystemGrassland", "pval"]; stars <- function(p) { if (p < 0.001) "***" else if (p < 0.01) "**" else if (p < 0.05) "*" else "" }; list(forest = paste0("Forest: \u03B2 = ", round(beta_forest, 3), stars(p_forest)), grass = paste0("Grassland: \u03B2 = ", round(beta_grass, 3), stars(p_grass))) }


# FUNCTIONS TO ADD LABELS
add_labels1 <- function(df) { df %>% dplyr::mutate(sig = dplyr::case_when(pval < 0.001 ~ "***", pval < 0.01 ~ "**", pval < 0.05 ~ "*", TRUE ~ "ns"), pct_val = round((exp(lnRR) - 1) * 100, 1), lab_k = paste0("(", k, ")"), lab_percent = paste0("(", pct_val, "% ", sig, ")")) }

add_labels2 <- function(df, metric_levels) { df %>% mutate(Metrics = factor(Metrics, levels = metric_levels), Restoration_strategy = factor(Restoration_strategy, levels = c("Passive", "Active")), sig = case_when(pval < 0.001 ~ "***", pval < 0.01 ~ "**", pval < 0.05 ~ "*", TRUE ~ "ns"), pct_val = round((exp(Estimate) - 1) * 100, 1), lab_k = paste0("(", K, ")"), lab_percent = paste0("(", Percentage, "% ", sig, ")")) }

```

## Restored vs Degraded

### Alpha diversity

```{r}
# OTU RICHNESS
## FIT MODEL
res_overall_otu_deg <- rma.mv(yi = yi,V = build_cov_matrix(otu_resvsdeg_df, rho = 0.5),random = ~ 1 | ID, method = "REML",data = otu_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(otu_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_otu_deg))

# REMOVE OUTLIERS IF ANY
outlier_otu <- get_outliers(res_overall_otu_deg, otu_resvsdeg_df)
otu_clean_df <- remove_outliers(otu_resvsdeg_df, outlier_otu)

## ECOSYSTEM-LEVEL MODELS
ecosystems_otu_deg <- split(otu_clean_df, otu_clean_df$Ecosystem)
res_ecosystem_otu_deg <- lapply(ecosystems_otu_deg, function(sub) { V_sub <- build_cov_matrix(sub, rho = 0.5) ;  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_otu_deg <- report_table(res_ecosystem_otu_deg, "OTU richness")
print(summary_otu_deg)
```

```{r}
# CHAO1 RICHNESS
## FIT MODEL
res_overall_chao1_deg <- rma.mv(yi = yi,V = build_cov_matrix(chao1_resvsdeg_df, rho = 0.5),random = ~ 1 | ID, method = "REML",data = chao1_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(chao1_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_chao1_deg))

# REMOVE OUTLIERS IF ANY
outlier_chao1 <- get_outliers(res_overall_chao1_deg, chao1_resvsdeg_df)
chao1_clean_df <- remove_outliers(chao1_resvsdeg_df, outlier_chao1)

## ECOSYSTEM-LEVEL MODELS
ecosystems_chao1_deg <- split(chao1_clean_df, chao1_clean_df$Ecosystem) 
res_ecosystem_chao1_deg <- lapply(ecosystems_chao1_deg, function(sub) { V_sub <- build_cov_matrix(sub, rho = 0.5); rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_chao1_deg <- report_table(res_ecosystem_chao1_deg, "Chao1 richness")
print(summary_chao1_deg)
```

```{r}
# SHANNON INDEX
## FIT MODEL
res_overall_shannon_deg <- rma.mv(yi = yi, V = build_cov_matrix(shannon_resvsdeg_df,rho=0.5),random = ~ 1 | ID, method = "REML",data = shannon_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(shannon_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_shannon_deg))

# REMOVE OUTLIERS IF ANY
outlier_shannon <- get_outliers(res_overall_shannon_deg, shannon_resvsdeg_df)
shannon_clean_df <- remove_outliers(shannon_resvsdeg_df, outlier_shannon)

## ECOSYSTEM-LEVEL MODELS
ecosystems_shannon_deg <- split(shannon_clean_df, shannon_clean_df$Ecosystem)
res_ecosystem_shannon_deg <- lapply(ecosystems_shannon_deg, function(sub) {  V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_shannon_deg <- report_table( res_ecosystem_shannon_deg,
                                                "Shannon index")
print(summary_shannon_deg)
```

```{r}
# SIMPSON INDEX
## FIT MODEL
res_overall_simpson_deg <- rma.mv(yi = yi, V = build_cov_matrix(simpson_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = simpson_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(simpson_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_simpson_deg))

# REMOVE OUTLIERS IF ANY
outlier_simpson <- get_outliers(res_overall_simpson_deg, simpson_resvsdeg_df)
simpson_clean_df <- remove_outliers(simpson_resvsdeg_df, outlier_simpson)

## ECOSYSTEM-LEVEL MODELS
ecosystems_simpson_deg <- split(simpson_clean_df, simpson_clean_df$Ecosystem)
res_ecosystem_simpson_deg <- lapply(ecosystems_simpson_deg, function(sub) {  V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_simpson_deg <- report_table(res_ecosystem_simpson_deg,
                                         "Simpson index")
print(summary_simpson_deg)
```

### Relative abundance

```{r}
# ASCOMYCOTA
## FIT MODEL
res_overall_asco_deg <- rma.mv(yi = yi, V = build_cov_matrix(asco_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = asco_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(asco_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_asco_deg))

# REMOVE OUTLIERS IF ANY
outlier_asco <- get_outliers(res_overall_asco_deg, asco_resvsdeg_df)
asco_clean_df <- remove_outliers(asco_resvsdeg_df, outlier_asco)

## ECOSYSTEM-LEVEL MODELS
ecosystems_asco_deg <- split(asco_clean_df, asco_clean_df$Ecosystem)
res_ecosystem_asco_deg <- lapply(ecosystems_asco_deg, function(sub) {  V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_asco_deg <- report_table(res_ecosystem_asco_deg,"Ascomycota")
print(summary_asco_deg)
```

```{r}
#### BASIDIOMYCOTA
## FIT MODEL
res_overall_basidio_deg <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = basidio_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(basidio_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_basidio_deg))

# REMOVE OUTLIERS IF ANY
outlier_basidio <- get_outliers(res_overall_basidio_deg, basidio_resvsdeg_df)
basidio_clean_df <- remove_outliers(basidio_resvsdeg_df, outlier_basidio)

## ECOSYSTEM-LEVEL MODELS
ecosystems_basidio_deg <- split(basidio_clean_df, basidio_clean_df$Ecosystem)
res_ecosystem_basidio_deg <- lapply(ecosystems_basidio_deg, function(sub) {  V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_basidio_deg <- report_table( res_ecosystem_basidio_deg, "Basidiomycota")
print(summary_basidio_deg)
```

### Composition

```{r}
# BETA DIVERISTY
## FIT MODEL
res_overall_beta_deg <- rma.mv( yi = yi,  V = build_cov_matrix(beta_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = beta_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(beta_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_beta_deg))

# REMOVE OUTLIERS IF ANY
outlier_beta <- get_outliers(res_overall_beta_deg, beta_resvsdeg_df)
beta_clean_df <- remove_outliers(beta_resvsdeg_df, outlier_beta)

## ECOSYSTEM-LEVEL MODELS
ecosystems_beta_deg <- split(beta_clean_df, beta_clean_df$Ecosystem)
res_ecosystem_beta_deg <- lapply(ecosystems_beta_deg, function(sub) {  V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_beta_deg <- report_table(res_ecosystem_beta_deg, "Beta diversity")
print(summary_beta_deg)
```

```{r}
# STRUCTURE
## FIT MODEL
res_overall_comp_deg <- rma.mv( yi = yi,  V = build_cov_matrix(comp_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = comp_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(comp_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_comp_deg))

# REMOVE OUTLIERS IF ANY
outlier_comp <- get_outliers(res_overall_comp_deg, comp_resvsdeg_df)
comp_clean_df <- remove_outliers(comp_resvsdeg_df, outlier_comp)

## ECOSYSTEM-LEVEL MODELS
ecosystems_comp_deg <- split(comp_clean_df, comp_clean_df$Ecosystem)
res_ecosystem_comp_deg <- lapply(ecosystems_comp_deg, function(sub) {  V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_comp_deg <- report_table(res_ecosystem_comp_deg,"Structure")
print(summary_comp_deg)
```

### Biomass

```{r}
# PLFA content
## FIT MODEL
res_overall_plfa_deg <- rma.mv( yi = yi,  V = build_cov_matrix(plfa_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = plfa_resvsdeg_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity_2(plfa_resvsdeg_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_plfa_deg))

# REMOVE OUTLIERS IF ANY
outlier_plfa <- get_outliers(res_overall_plfa_deg, plfa_resvsdeg_df)
plfa_clean_df <- remove_outliers(plfa_resvsdeg_df, outlier_plfa)

## ECOSYSTEM-LEVEL MODELS
ecosystems_plfa_deg <- split(plfa_clean_df, plfa_clean_df$Ecosystem) 
res_ecosystem_plfa_deg <- lapply(ecosystems_plfa_deg, function(sub) {  V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_plfa_deg <- report_table(res_ecosystem_plfa_deg, "PLFA content")
print(summary_plfa_deg)
```

```{r}
metrics_resvsdeg_df <- rbind(summary_otu_deg, summary_chao1_deg,summary_shannon_deg, summary_simpson_deg,summary_asco_deg, summary_basidio_deg, summary_beta_deg, summary_comp_deg,summary_plfa_deg)
print(metrics_resvsdeg_df)
```

```{r}
write.csv(file = "data/figure_data/overall_resvsdeg_df.csv", metrics_resvsdeg_df, row.names = FALSE )

```

### Figure 3.1

```{r warning=FALSE}
# LOAD DATA
metrics_resvsdeg_df <- read.csv("data/figure_data/overall_resvsdeg_df.csv", header = TRUE)

# SEPARATE DATA
alpha_diversity_deg <- metrics_resvsdeg_df[1:8,]
relabun_deg         <- metrics_resvsdeg_df[9:12,]
comm_deg            <- metrics_resvsdeg_df[13:16,]
plfa_deg            <- metrics_resvsdeg_df[17:18,]

alpha_diversity_deg <- add_labels1(alpha_diversity_deg)
relabun_deg         <- add_labels1(relabun_deg)
comm_deg            <- add_labels1(comm_deg)
plfa_deg  <- add_labels1(plfa_deg)

# ALPHA DIVERSITY
label_alpha <- data.frame(label = c("Simpson index", "Shannon index", "Chao1 richness", "OTU richness"), y = c(1.45, 2.45, 3.45, 4.45),  x = -0.6 )

alpha_diversity_deg$Metric <- factor(alpha_diversity_deg$Metric, levels = c("Simpson index", "Shannon index", "Chao1 richness", "OTU richness"))

overall_alpha_diversity_deg_plot <- ggplot(alpha_diversity_deg, aes(x = lnRR, y = Metric, color = Ecosystem)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.5), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.5)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + geom_text(data = label_alpha, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "lnRR (alpha diversity)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))

## RELATIVE ABUNDANCE PLOT
label_rel <- data.frame(label = c("Basidiomycota", "Ascomycota"),y = c(1.45, 2.45),  x = -1)
relabun_deg$Metric <- factor(relabun_deg$Metric, levels = c("Basidiomycota", "Ascomycota"))

overall_relabun_deg_plot <- ggplot(relabun_deg, aes(x = lnRR, y = Metric, color = Ecosystem)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.5), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.5)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + geom_text(data = label_rel, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "lnRR (relative abundance)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))

## COMPOSITION PLOT
label_comm <- data.frame(label = c("Beta diversity", "Structure"),  y = c(1.45, 2.45),  x = -1.5)

comm_deg$Metric <- factor(comm_deg$Metric,levels = c("Beta diversity", "Structure"))

overall_comm_deg_plot <- ggplot(comm_deg, aes(x = lnRR, y = Metric, color = Ecosystem)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.5), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.5)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + geom_text(data = label_comm, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "lnRR (composition)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))


## BIOMASS PLOT
label_plfa <- data.frame(label = c("PLFA content"), y = c(1.45),  x = -1)
overall_biomass_deg_plot <- ggplot(plfa_deg, aes(x = lnRR, y = Metric, color = Ecosystem)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.5), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.5)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + geom_text(data = label_plfa, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "lnRR (biomass)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))
```

```{r warning=FALSE, message=FALSE}
legend <- get_legend(overall_biomass_deg_plot + theme(legend.position = "bottom",  legend.text = element_text(size = 12), legend.title = element_text(size = 12), legend.margin = margin(t = -20)) + labs(color = "Ecosystem"))
Figure_3_deg1<-ggarrange(overall_alpha_diversity_deg_plot,  overall_biomass_deg_plot,  nrow = 2, heights = c(1, 0.4), legend = "none")
Figure_3_deg2 <-ggarrange(overall_relabun_deg_plot, overall_comm_deg_plot,nrow = 2, legend = "none")
Figure_3_deg_grid <- ggarrange(Figure_3_deg1, Figure_3_deg2, ncol = 2)
final_combined <- plot_grid(Figure_3_deg_grid, legend, ncol = 1,  rel_heights = c(1, 0.08))
Figure_3.1 <- annotate_figure(final_combined, top = text_grob("Restored vs Degraded", face = "bold", size = 12), fig.lab = "(a)", fig.lab.pos = "top.right", fig.lab.face = "bold", fig.lab.size = 16)
Figure_3.1
```

```{r eval=FALSE}
ggsave("../Figure_3.1.tiff", plot = Figure_3.1, dpi = 600, height = 6, width = 5)
```

## Restored vs Reference

### Alpha diversity

```{r}
# OTU RICHNESS
## FIT MODEL
res_overall_otu_ref <- rma.mv(  yi = yi,  V = build_cov_matrix(otu_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = otu_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(otu_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_otu_ref))

# REMOVE OUTLIERS IF ANY
outlier_otu_ref <- get_outliers(res_overall_otu_ref, otu_resvsref_df)
otu_clean_ref_df <- remove_outliers(otu_resvsref_df, outlier_otu_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_otu_ref <- split(otu_clean_ref_df, otu_clean_ref_df$Ecosystem)
res_ecosystem_otu_ref <- lapply(ecosystems_otu_ref, function(sub) {  V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_otu_ref <- report_table(res_ecosystem_otu_ref,  "OTU richness")
print(summary_otu_ref)
```

```{r}
# CHAO1 RICHNESS
## FIT MODEL
res_overall_chao1_ref <- rma.mv(  yi = yi,  V = build_cov_matrix(chao1_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = chao1_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(chao1_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_chao1_ref))

# REMOVE OUTLIERS IF ANY
outlier_chao1_ref <- get_outliers(res_overall_chao1_ref, chao1_resvsref_df)
chao1_clean_ref_df <- remove_outliers(chao1_resvsref_df, outlier_chao1_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_chao1_ref <- split(chao1_clean_ref_df, chao1_clean_ref_df$Ecosystem)
res_ecosystem_chao1_ref <- lapply(ecosystems_chao1_ref, function(sub) {V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_chao1_ref <- report_table(res_ecosystem_chao1_ref, "Chao1 richness")
print(summary_chao1_ref)
```

```{r}
# SHANNON INDEX
## FIT MODEL
res_overall_shannon_ref <- rma.mv(  yi = yi,  V = build_cov_matrix(shannon_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = shannon_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(shannon_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_shannon_ref))

# REMOVE OUTLIERS IF ANY
outlier_shannon_ref <- get_outliers(res_overall_shannon_ref, shannon_resvsref_df)
shannon_clean_ref_df <- remove_outliers(shannon_resvsref_df, outlier_shannon_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_shannon_ref <-split(shannon_clean_ref_df, shannon_clean_ref_df$Ecosystem)
res_ecosystem_shannon_ref <- lapply(ecosystems_shannon_ref, function(sub) {V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_shannon_ref <- report_table(res_ecosystem_shannon_ref,"Shannon index")
print(summary_shannon_ref)
```

```{r}
# SIMPSON INDEX
## FIT MODEL
res_overall_simpson_ref <- rma.mv(  yi = yi,  V = build_cov_matrix(simpson_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = simpson_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(simpson_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_simpson_ref))

# REMOVE OUTLIERS IF ANY
outlier_simpson_ref <- get_outliers(res_overall_simpson_ref, simpson_resvsref_df)
simpson_clean_ref_df <- remove_outliers(simpson_resvsref_df, outlier_simpson_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_simpson_ref <-split(simpson_clean_ref_df, simpson_clean_ref_df$Ecosystem)
res_ecosystem_simpson_ref <- lapply(ecosystems_simpson_ref, function(sub) {V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_simpson_ref <- report_table(res_ecosystem_simpson_ref, "Simpson index")
print(summary_simpson_ref)
```

### Relative abundance

```{r}
# ASCOMYCOTA
## FIT MODEL
res_overall_asco_ref <- rma.mv(yi = yi,  V = build_cov_matrix(asco_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = asco_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(asco_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_asco_ref))

# REMOVE OUTLIERS IF ANY
outlier_asco_ref <- get_outliers(res_overall_asco_ref, asco_resvsref_df)
asco_clean_ref_df <- remove_outliers(asco_resvsref_df, outlier_asco_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_asco_ref <- split(asco_clean_ref_df, asco_clean_ref_df$Ecosystem)
res_ecosystem_asco_ref <- lapply(ecosystems_asco_ref, function(sub) {V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_asco_ref <- report_table(res_ecosystem_asco_ref,  "Ascomycota")
print(summary_asco_ref)
```

```{r}
# BASIDIOMYCOTA
## FIT MODEL
res_overall_basidio_ref <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = basidio_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(basidio_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_basidio_ref))

# REMOVE OUTLIERS IF ANY
outlier_basidio_ref <- get_outliers(res_overall_basidio_ref, basidio_resvsref_df)
basidio_clean_ref_df <- remove_outliers(basidio_resvsref_df, outlier_basidio_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_basidio_ref <-split(basidio_clean_ref_df, basidio_clean_ref_df$Ecosystem)
res_ecosystem_basidio_ref <- lapply(ecosystems_basidio_ref, function(sub) {V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_basidio_ref <- report_table(res_ecosystem_basidio_ref,"Basidiomycota")
print(summary_basidio_ref)
```

### Composition

```{r}
# BETA DIVERSITY
## FIT MODEL
res_overall_beta_ref <- rma.mv(  yi = yi,  V = build_cov_matrix(beta_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = beta_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(beta_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_beta_ref))

# REMOVE OUTLIERS IF ANY
outlier_beta_ref <- get_outliers(res_overall_beta_ref, beta_resvsref_df)
beta_clean_ref_df <- remove_outliers(beta_resvsref_df, outlier_beta_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_beta_ref <- split(beta_clean_ref_df, beta_clean_ref_df$Ecosystem)
res_ecosystem_beta_ref <- lapply(ecosystems_beta_ref, function(sub) {V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_beta_ref <- report_table(res_ecosystem_beta_ref,"Beta diversity")
print(summary_beta_ref)
```

```{r}
# STRUCTURE
## FIT MODEL
res_overall_comp_ref <- rma.mv(  yi = yi,  V = build_cov_matrix(comp_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = comp_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(comp_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_comp_ref))

# REMOVE OUTLIERS IF ANY
outlier_comp_ref <- get_outliers(res_overall_comp_ref, comp_resvsref_df)
comp_clean_ref_df <- remove_outliers(comp_resvsref_df, outlier_comp_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_comp_ref <- split(comp_clean_ref_df, comp_clean_ref_df$Ecosystem) 
res_ecosystem_comp_ref <- lapply(ecosystems_comp_ref, function(sub) {V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_comp_ref <- report_table(res_ecosystem_comp_ref,  "Structure")
print(summary_comp_ref)
```

### Biomass

```{r}
# PLFA CONTENT
## FIT MODEL
res_overall_plfa_ref <- rma.mv(yi = yi,  V = build_cov_matrix(plfa_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = plfa_resvsref_df)

# SENSITIVITY ANALYSIS
print(run_sensitivity(plfa_resvsref_df))

# GET TEST OF HETEROGENEITY
print(get_heterogeneity(res_overall_plfa_ref))

# REMOVE OUTLIERS IF ANY
outlier_plfa_ref <- get_outliers(res_overall_plfa_ref, plfa_resvsref_df)
plfa_clean_ref_df <- remove_outliers(plfa_resvsref_df, outlier_plfa_ref)

## ECOSYSTEM-LEVEL MODELS
ecosystems_plfa_ref <- split(plfa_clean_ref_df, plfa_clean_ref_df$Ecosystem)
res_ecosystem_plfa_ref <- lapply(ecosystems_plfa_ref, function(sub) {V_sub <- build_cov_matrix(sub, rho = 0.5);  rma.mv(yi = yi, V = V_sub, random = ~ 1 | ID, method = "REML", data = sub)})

## REPORTING TABLE
summary_plfa_ref <- report_table(res_ecosystem_plfa_ref,  "PLFA content")
print(summary_plfa_ref)
```

```{r}
metrics_resvsref_df <- rbind( summary_otu_ref,  summary_chao1_ref, summary_shannon_ref,  summary_simpson_ref, summary_asco_ref,  summary_basidio_ref, summary_beta_ref,  summary_comp_ref, summary_plfa_ref)
print(metrics_resvsref_df)
```

```{r eval=FALSE}
write.csv(file = "data/figure_data/overall_resvsref_df.csv", metrics_resvsref_df, row.names = FALSE )
```

### Figure 3.2

```{r}
metrics_resvsref_df <- read.csv("data/figure_data/overall_resvsref_df.csv",  header = TRUE)

alpha_diversity_ref <- metrics_resvsref_df[1:8,]
relabun_ref         <- metrics_resvsref_df[9:12,]
comm_ref            <- metrics_resvsref_df[13:16,]
plfa_ref            <- metrics_resvsref_df[17:18,]

alpha_diversity_ref <- add_labels1(alpha_diversity_ref)
relabun_ref         <- add_labels1(relabun_ref)
comm_ref            <- add_labels1(comm_ref)
plfa_ref            <- add_labels1(plfa_ref)


# ALPHA DIVERSITY
label_alpha <- data.frame(label = c("Simpson index", "Shannon index", "Chao1 richness", "OTU richness"), y = c(1.45, 2.45, 3.45, 4.45),  x = -0.6 )

alpha_diversity_ref$Metric <- factor(alpha_diversity_ref$Metric, levels = c("Simpson index", "Shannon index", "Chao1 richness", "OTU richness"))
overall_alpha_diversity_ref_plot <- ggplot(alpha_diversity_ref, aes(x = lnRR, y = Metric, color = Ecosystem)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.5), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.5)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + geom_text(data = label_alpha, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "lnRR (alpha diversity)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.05, 0.5)))

## RELATIVE ABUNDANCE
label_rel <- data.frame(label = c("Basidiomycota", "Ascomycota"), y = c(1.45, 2.45),  x = -1)
relabun_ref$Metric <- factor(relabun_ref$Metric, levels = c("Basidiomycota", "Ascomycota"))

overall_relabun_ref_plot <- ggplot(relabun_ref, aes(x = lnRR, y = Metric, color = Ecosystem)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.5), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.5)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + geom_text(data = label_rel, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "lnRR (relative abundance)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))

## COMPOSITION
label_comm <- data.frame(label = c("Structure", "Beta diversity"), y = c(1.45, 2.45),    x = -1.5)
comm_ref$Metric <- factor(comm_ref$Metric, levels = c("Structure", "Beta diversity"))

overall_comm_ref_plot <- ggplot(comm_ref, aes(x = lnRR, y = Metric, color = Ecosystem)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.5), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.5)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + geom_text(data = label_comm, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "lnRR (composition)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.6)))

## PLFA CONTENT
label_plfa <- data.frame(label = c("PLFA content"), y = c(1.45),  x = -1)

overall_biomass_ref_plot <- ggplot(plfa_ref, aes(x = lnRR, y = Metric, color = Ecosystem)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.5), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.5)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + geom_text(data = label_plfa, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "lnRR (biomass)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))
```

```{r}
master_legend_ref <- get_legend(overall_biomass_ref_plot + theme(legend.position = "bottom", legend.text = element_text(size = 12), legend.title = element_text(size = 12, face = "plain"), legend.margin = margin(t = -20, r = 0, b = 0, l = 0)) + labs(color = "Ecosystem"))
Figure_3_ref1 <- ggarrange( overall_alpha_diversity_ref_plot, overall_biomass_ref_plot, nrow = 2, heights = c(1, 0.4),legend = "none")
Figure_3_ref2 <- ggarrange( overall_relabun_ref_plot, overall_comm_ref_plot,  nrow = 2, heights = c(1, 1),legend = "none")
Figure_3_ref_grid <- ggarrange( Figure_3_ref1, Figure_3_ref2,  ncol = 2, widths = c(1, 1))
final_combined_ref <- plot_grid(Figure_3_ref_grid, master_legend_ref, ncol = 1, rel_heights = c(1, 0.08))
Figure_3.2 <- annotate_figure( final_combined_ref,  top = text_grob("Restored vs Reference", face = "bold", size = 12),  fig.lab = "(b)",  fig.lab.pos = "top.right",fig.lab.face = "bold",  fig.lab.size = 16)
Figure_3.2
```

```{r eval=FALSE}
ggsave("../Figure_3.2.tiff", plot = Figure_3.2, dpi = 600, height = 6, width = 5)
```

# Chapter VIII: Effect of restoration strategies

### Restored vs Degraded

#### Alpha diversity

```{r}
# OTU RICHNESS
## FIT MODEL
res_otu_init <- rma.mv(yi = yi, V = build_cov_matrix(otu_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = otu_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_otu_deg <- get_outliers(res_otu_init, otu_resvsdeg_df)
otu_filtered <- remove_outliers(otu_resvsdeg_df, outlier_otu_deg)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
otu_filtered$Restoration_strategy <- relevel(factor(otu_filtered$Restoration_strategy), ref = "Active")
res_active_otu <- rma.mv(yi = yi, V = build_cov_matrix(otu_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem +  Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = otu_filtered)

### Passive as reference (Intercept = Passive)
otu_filtered$Restoration_strategy <- relevel(factor(otu_filtered$Restoration_strategy), ref = "Passive")
res_passive_otu <- rma.mv(yi = yi, V = build_cov_matrix(otu_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem +  Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = otu_filtered)
summary(res_passive_otu)

## REPORTING TABLE
estimates_df_otu <- rbind(get_results(res_active_otu, otu_filtered, "Passive"),  get_results(res_passive_otu, otu_filtered, "Active")) %>%  mutate(Metrics = "OTU richness")
print(estimates_df_otu)
```

```{r}
# CHAO1 RICHNESS
## FIT MODEL
res_chao1_init <- rma.mv(yi = yi, V = build_cov_matrix(chao1_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = chao1_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_chao1_deg <- get_outliers(res_chao1_init, chao1_resvsdeg_df)
chao1_filtered <- remove_outliers(chao1_resvsdeg_df, outlier_chao1_deg)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
chao1_filtered$Restoration_strategy <- relevel(factor(chao1_filtered$Restoration_strategy), ref = "Active")
res_active_chao1 <- rma.mv(yi = yi, V = build_cov_matrix(chao1_filtered, rho = 0.5),mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = chao1_filtered)

### Passive as reference (Intercept = Passive)
chao1_filtered$Restoration_strategy <- relevel(factor(chao1_filtered$Restoration_strategy), ref = "Passive")
res_passive_chao1 <- rma.mv(yi = yi, V = build_cov_matrix(chao1_filtered, rho = 0.5),mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML",  data = chao1_filtered)
summary(res_passive_chao1)

## REPORTING TABLE
estimates_df_chao1 <- rbind(get_results(res_passive_chao1, chao1_filtered, "Passive"),  get_results(res_active_chao1, chao1_filtered, "Active")) %>%  mutate(Metrics = "Chao1 richness")
print(estimates_df_chao1)
```

```{r}
# SHANNON INDEX
## FIT MODEL
res_shannon_init <- rma.mv(yi = yi, V = build_cov_matrix(shannon_resvsdeg_df, rho = 0.5),mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = shannon_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_shannon_deg <- get_outliers(res_shannon_init, shannon_resvsdeg_df)
shannon_filtered <- remove_outliers(shannon_resvsdeg_df, outlier_shannon_deg)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
shannon_filtered$Restoration_strategy <- relevel(factor(shannon_filtered$Restoration_strategy), ref = "Active")
res_active_shannon <- rma.mv(yi = yi, V = build_cov_matrix(shannon_filtered, rho = 0.5),mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = shannon_filtered)

### Passive as reference (Intercept = Passive)
shannon_filtered$Restoration_strategy <- relevel(factor(shannon_filtered$Restoration_strategy), ref = "Passive")
res_passive_shannon <- rma.mv(yi = yi, V = build_cov_matrix(shannon_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = shannon_filtered) 
summary(res_passive_shannon)

## REPORTING TABLE
estimates_df_shannon <- rbind(get_results(res_passive_shannon, shannon_filtered, "Passive"),  get_results(res_active_shannon, shannon_filtered, "Active")) %>%  mutate(Metrics = "Shannon index")
print(estimates_df_shannon)
```

```{r}
# SIMPSON INDEX
## FIT MODEL
res_simpson_init <- rma.mv(yi = yi, V = build_cov_matrix(simpson_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = simpson_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_simpson_deg <- get_outliers(res_simpson_init, simpson_resvsdeg_df)
simpson_filtered <- remove_outliers(simpson_resvsdeg_df, outlier_simpson_deg)

# FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
simpson_filtered$Restoration_strategy <- relevel(factor(simpson_filtered$Restoration_strategy), ref = "Active")
res_active_simpson <- rma.mv(yi = yi, V = build_cov_matrix(simpson_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML",  data = simpson_filtered)
summary(res_active_simpson)

### Passive as reference (Intercept = Passive)
simpson_filtered$Restoration_strategy <- relevel(factor(simpson_filtered$Restoration_strategy), ref = "Passive")
res_passive_simpson <- rma.mv(yi = yi, V = build_cov_matrix(simpson_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = simpson_filtered)

## REPORTING TABLE
estimates_df_simpson <- rbind(get_results(res_passive_simpson, simpson_filtered, "Passive"), get_results(res_active_simpson, simpson_filtered, "Active")) %>%  mutate(Metrics = "Simpson index")
print(estimates_df_simpson)
```

#### Relative abundance

```{r}
# ASCOMYCOTA
## FIT MODEL
res_asco_init <- rma.mv(yi = yi, V =  build_cov_matrix(asco_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = asco_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_asco_deg <- get_outliers(res_asco_init, asco_resvsdeg_df)
asco_filtered <- remove_outliers(asco_resvsdeg_df, outlier_asco_deg)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
asco_filtered$Restoration_strategy <- relevel(factor(asco_filtered$Restoration_strategy), ref = "Active")
res_active_asco <- rma.mv(yi = yi, V = build_cov_matrix(asco_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML",  data = asco_filtered)

### Passive as reference (Intercept = Passive)
asco_filtered$Restoration_strategy <- relevel(factor(asco_filtered$Restoration_strategy), ref = "Passive")
res_passive_asco <- rma.mv(yi = yi, V = build_cov_matrix(asco_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = asco_filtered)

## REPORTING TABLE 
estimates_df_asco <- rbind( get_results(res_passive_asco, asco_filtered, "Passive"), get_results(res_active_asco, asco_filtered, "Active")) %>% mutate(Metrics = "Ascomycota")
print(estimates_df_asco)
```

```{r}
# BASIDIOMYCOTA
## FIT MODEL
res_basidio_init <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = basidio_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_basidio_deg <- get_outliers(res_basidio_init, basidio_resvsdeg_df)
basidio_filtered <- remove_outliers(basidio_resvsdeg_df, outlier_basidio_deg)

# FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
basidio_filtered$Restoration_strategy <- relevel(factor(basidio_filtered$Restoration_strategy), ref = "Active")
res_active_basidio <- rma.mv(yi = yi, V = build_cov_matrix(basidio_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem +  Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = basidio_filtered)

### Passive as reference (Intercept = Passive)
basidio_filtered$Restoration_strategy <- relevel(factor(basidio_filtered$Restoration_strategy), ref = "Passive")
res_passive_basidio <- rma.mv(yi = yi, V = build_cov_matrix(basidio_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = basidio_filtered)
summary(res_passive_basidio)

## REPORTING TABLE
estimates_df_basidio <- rbind(get_results(res_passive_basidio, basidio_filtered, "Passive"),  get_results(res_active_basidio, basidio_filtered, "Active")) %>%  mutate(Metrics = "Basidiomycota")
print(estimates_df_basidio)
```

#### Composition

```{r}
# BETA DIVERSITY
## FIT MODEL
res_beta_init <- rma.mv(yi = yi, V = build_cov_matrix(beta_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = beta_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_beta_deg <- get_outliers(res_beta_init, beta_resvsdeg_df)
beta_filtered <- remove_outliers(beta_resvsdeg_df, outlier_beta_deg)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
beta_filtered$Restoration_strategy <- relevel(factor(beta_filtered$Restoration_strategy), ref = "Active")
res_active_beta <- rma.mv(yi = yi, V = build_cov_matrix(beta_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = beta_filtered)

### Passive as reference (Intercept = Passive)
beta_filtered$Restoration_strategy <- relevel(factor(beta_filtered$Restoration_strategy), ref = "Passive")
res_passive_beta <- rma.mv(yi = yi, V = build_cov_matrix(beta_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem +  Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = beta_filtered)

## REPORTING TABLE
estimates_df_beta <- rbind(get_results(res_passive_beta, beta_filtered, "Passive"),  get_results(res_active_beta, beta_filtered, "Active")) %>%  mutate(Metrics = "Beta diversity")
print(estimates_df_beta)
```

```{r}
# STRUCTURE
## FIT MODEL
res_comp_init <- rma.mv(yi = yi, V = build_cov_matrix(comp_resvsdeg_df, rho = 0.5),mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,random = ~ 1 | ID, method = "REML", data = comp_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_comp_deg <- get_outliers(res_comp_init, comp_resvsdeg_df)
comp_filtered <- remove_outliers(comp_resvsdeg_df, outlier_comp_deg)

# FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
comp_filtered$Restoration_strategy <- relevel(factor(comp_filtered$Restoration_strategy), ref = "Active")
res_active_comp <- rma.mv(yi = yi, V = build_cov_matrix(comp_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,random = ~ 1 | ID, method = "REML", data = comp_filtered)

### Passive as reference (Intercept = Passive)
comp_filtered$Restoration_strategy <- relevel(factor(comp_filtered$Restoration_strategy), ref = "Passive")
res_passive_comp <- rma.mv(yi = yi, V = build_cov_matrix(comp_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID, method = "REML", data = comp_filtered)

## REPORTING TABLE
estimates_df_comp <- rbind(get_results(res_passive_comp, comp_filtered, "Passive"),  get_results(res_active_comp, comp_filtered, "Active")) %>%  mutate(Metrics = "Structure")
print(estimates_df_comp)
```

#### Biomass

```{r}
# PLFA CONTENT
## FIT MODEL
res_plfa_init <- rma.mv(yi = yi, V = build_cov_matrix(plfa_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = plfa_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_plfa_deg <- get_outliers(res_plfa_init, plfa_resvsdeg_df)
plfa_filtered <- remove_outliers(plfa_resvsdeg_df, outlier_plfa_deg)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
plfa_filtered$Restoration_strategy <- relevel(factor(plfa_filtered$Restoration_strategy), ref = "Active")
res_active_plfa <- rma.mv(yi = yi, V = build_cov_matrix(plfa_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML",  data = plfa_filtered)

### Passive as reference (Intercept = Passive)
plfa_filtered$Restoration_strategy <- relevel(factor(plfa_filtered$Restoration_strategy), ref = "Passive")
res_passive_plfa <- rma.mv(yi = yi, V = build_cov_matrix(plfa_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem +Prior_land_use + Restoration_time,random = ~ 1 | ID, method = "REML",  data = plfa_filtered)

## REPORTING TABLE
estimates_df_plfa <- rbind(get_results(res_passive_plfa, plfa_filtered, "Passive"),  get_results(res_active_plfa, plfa_filtered, "Active")) %>%  mutate(Metrics = "PLFA content")
print(estimates_df_plfa)
```

```{r eval=FALSE}
strategy_resvsdeg_df <- rbind(estimates_df_otu,  estimates_df_chao1, estimates_df_shannon,  estimates_df_simpson, estimates_df_asco,  estimates_df_basidio, estimates_df_beta, estimates_df_comp, estimates_df_plfa)
print(strategy_resvsdeg_df)
```

```{r eval=FALSE}
write.csv(file = "data/figure_data/strategy_resvsdeg_df.csv", strategy_resvsdeg_df, row.names = FALSE )
```

#### Figure 4.1

```{r warning=FALSE}
strategy_resvsdeg_df <- read.csv("data/figure_data/strategy_resvsdeg_df.csv", header = TRUE)

alpha_restoration_deg          <- strategy_resvsdeg_df[1:8,]
relabund_restoration_deg         <- strategy_resvsdeg_df[9:12,]
comm_restoration_deg            <- strategy_resvsdeg_df[13:16,]
plfa_restoration_deg            <- strategy_resvsdeg_df[17:18,]

# FORMAT DATA
alpha_restoration_deg <- add_labels2(alpha_restoration_deg, c("OTU richness", "Chao1 richness", "Shannon index", "Simpson index"))
relabund_restoration_deg <- add_labels2( relabund_restoration_deg, c("Ascomycota", "Basidiomycota"))
comm_restoration_deg <- add_labels2(comm_restoration_deg, c("Structure", "Beta diversity"))
plfa_restoration_deg <- add_labels2(plfa_restoration_deg, c("PLFA content"))

# ALPHA DIVERSITY PLOT
alpha_restoration_deg$Metrics <- factor(alpha_restoration_deg$Metrics,levels = c("Simpson index", "Shannon index", "Chao1 richness", "OTU richness"))
label_df <- data.frame(label = c("OTU richness", "Chao1 richness", "Shannon index", "Simpson index"),y = c(4.45, 3.45, 2.45, 1.45), x = -1 )

alpha_diversity_deg_plot <- ggplot(alpha_restoration_deg, aes(x = Estimate, y = Metrics, color = Restoration_strategy)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.6), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height = 0.2, position = position_dodge(width = 0.6)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.6), hjust = 1.2, size = 3.0, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.6), hjust = -0.15, size = 3.0, show.legend = FALSE) + geom_text(data = label_df, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Passive" = "darkgreen", "Active" = "maroon")) + labs(x = "lnRR (alpha diversity)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))

# RELATIVE ABUNDANCE PLOT
relabund_restoration_deg$Metrics <- factor(relabund_restoration_deg$Metrics,levels = c("Basidiomycota", "Ascomycota"))
label_df_rel <- data.frame( label = c("Ascomycota", "Basidiomycota"), y = c(2.45, 1.45),  x = -2 )

relabun_deg_plot <- ggplot(relabund_restoration_deg, aes(x = Estimate, y = Metrics, color = Restoration_strategy)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.6), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height = 0.2, position = position_dodge(width = 0.6)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.6), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.6), hjust = -0.15, size = 3.2, show.legend = FALSE) + geom_text(data = label_df_rel, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Passive" = "darkgreen", "Active" = "maroon")) + labs(x = "lnRR (relative abundance)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))

# COMPOSITION PLOT
comm_restoration_deg$Metrics <- factor(comm_restoration_deg$Metrics,  levels = c("Beta diversity", "Structure"))
label_df_comm <- data.frame(label = c("Structure", "Beta diversity"), y = c(2.45, 1.45),  x = -2)

comm_deg_plot <- ggplot(comm_restoration_deg, aes(x = Estimate, y = Metrics, color = Restoration_strategy)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.6), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height = 0.2, position = position_dodge(width = 0.6)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.6), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.6), hjust = -0.15, size = 3.2, show.legend = FALSE) + geom_text(data = label_df_comm, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Passive" = "darkgreen", "Active" = "maroon")) + labs(x = "lnRR (composition)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.5)))

# BIOMASS PLOT
label_df_plfa <- data.frame(label = c("PLFA content"),y = 1.45, x = -2)

plfa_restoration_deg_plot <- ggplot(plfa_restoration_deg, aes(x = Estimate, y = Metrics, color = Restoration_strategy)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.6), size = 3) + geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), height = 0.2, position = position_dodge(width = 0.6)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.6), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.6), hjust = -0.15, size = 3.2, show.legend = FALSE) + geom_text(data = label_df_plfa, aes(x = x, y = y, label = label), color = "black", size = 3.5, fontface = "plain", inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Passive" = "darkgreen", "Active" = "maroon")) + labs(x = "lnRR (biomass)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.55)))
```

```{r warning=FALSE, message=FALSE}
# UNIFY LEGEND & THEME
shared_plot_for_legend <- alpha_diversity_deg_plot + theme(legend.position = "bottom") + scale_color_manual(name = "Restoration strategy", values = c("Passive" = "darkgreen", "Active" = "maroon"), labels = c("Passive" = "Natural regeneration", "Active" = "Active restoration"))

legend_bottom <- get_legend(shared_plot_for_legend)
Figure_4_deg_left <- ggarrange(alpha_diversity_deg_plot + theme(legend.position = "none"), plfa_restoration_deg_plot + theme(legend.position = "none"), ncol = 1,  heights = c(1, 0.5), align = "v")
Figure_4_deg_right <- ggarrange(relabun_deg_plot + theme(legend.position = "none"), comm_deg_plot + theme(legend.position = "none"), ncol = 1, heights = c(1, 1), align = "v")
Figure_4.1 <- grid.arrange( Figure_4_deg_left, Figure_4_deg_right, ncol = 2, widths = c(1, 1), bottom = legend_bottom, top = textGrob("Restored vs Degraded", gp = gpar(fontsize = 12, fontface = "bold")))
Figure_4.1 <- annotate_figure(Figure_4.1, fig.lab = "(a)", fig.lab.pos = "top.right",fig.lab.face = "bold", fig.lab.size = 16)
```

```{r eval=FALSE}
ggsave("../Figure_4.1.tiff", plot = Figure_4.1, dpi = 600, height = 6, width = 5)
```

## Restored vs Reference

#### Alpha diversity

```{r}
# OTU RICHNESS
## FIT MODEL
res_otu_ref_init <- rma.mv(yi = yi,  V = build_cov_matrix(otu_resvsref_df, rho = 0.5), mods = ~ Restoration_strategy +  Ecosystem + Prior_land_use + Restoration_time,random = ~ 1 | ID, method = "REML", data = otu_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_otu_ref <- get_outliers(res_otu_init, otu_resvsref_df)
otu_ref_filtered <- remove_outliers(otu_resvsref_df, outlier_otu_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
otu_ref_filtered$Restoration_strategy <- relevel(factor(otu_ref_filtered$Restoration_strategy), ref = "Active")
mod_ref_active <- rma.mv(yi = yi, V = build_cov_matrix(otu_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = otu_ref_filtered)

### NATURAL REGENERAITON AS REFERENCE
otu_ref_filtered$Restoration_strategy <- relevel(factor(otu_ref_filtered$Restoration_strategy), ref = "Passive")
mod_ref_passive <- rma.mv(yi = yi, V = build_cov_matrix(otu_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = otu_ref_filtered)

## REPORTING TABLE
estimates_ref_otu <- rbind(get_results(mod_ref_passive, otu_ref_filtered, "Passive"),  get_results(mod_ref_active, otu_ref_filtered, "Active")) %>%  mutate(Metrics = "OTU richness")
print(estimates_ref_otu)
```

```{r}
# CHAO1 RICHNESS
res_chao1_ref_init <- rma.mv(yi = yi, V = build_cov_matrix(chao1_resvsref_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = chao1_resvsref_df)

# REMOVE OUTLIERS IF ANY
outlier_chao1_ref <- get_outliers(res_chao1_init, chao1_resvsref_df)
chao1_ref_filtered <- remove_outliers(chao1_resvsref_df, outlier_chao1_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
chao1_ref_filtered$Restoration_strategy <- relevel(factor(chao1_ref_filtered$Restoration_strategy), ref = "Active")
mod_chao1_ref_active <- rma.mv(yi = yi, V = build_cov_matrix(chao1_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = chao1_ref_filtered)

### Passive as reference (Intercept = Passive)
chao1_ref_filtered$Restoration_strategy <- relevel(factor(chao1_ref_filtered$Restoration_strategy), ref = "Passive")
mod_chao1_ref_passive <- rma.mv(yi = yi,  V = build_cov_matrix(chao1_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = chao1_ref_filtered)

## REPORTING TABLE
estimates_ref_chao1 <- rbind(get_results(mod_chao1_ref_passive, chao1_ref_filtered, "Passive"), get_results(mod_chao1_ref_active, chao1_ref_filtered, "Active")) %>%  mutate(Metrics = "Chao1 richness")
print(estimates_ref_chao1)
```

```{r}
# SHANNON INDEX
## FIT MODEL
res_shannon_ref_init <- rma.mv(yi = yi,  V = build_cov_matrix(shannon_resvsref_df, rho = 0.5),mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = shannon_resvsref_df)

# REMOVE OUTLIERS IF ANY
outlier_shannon_ref <- get_outliers(res_shannon_init, shannon_resvsref_df)
shannon_ref_filtered <- remove_outliers(shannon_resvsref_df, outlier_shannon_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
shannon_ref_filtered$Restoration_strategy <- relevel(factor(shannon_ref_filtered$Restoration_strategy), ref = "Active")
mod_shannon_ref_active <- rma.mv(yi = yi, V = build_cov_matrix(shannon_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = shannon_ref_filtered)

### Passive as reference (Intercept = Passive)
shannon_ref_filtered$Restoration_strategy <- relevel(factor(shannon_ref_filtered$Restoration_strategy), ref = "Passive")
mod_shannon_ref_passive <- rma.mv(yi = yi, V = build_cov_matrix(shannon_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem +  Prior_land_use + Restoration_time, random = ~ 1 | ID, data = shannon_ref_filtered)

## REPORTING TABLE
estimates_ref_shannon <- rbind(get_results(mod_shannon_ref_passive, shannon_ref_filtered, "Passive"),  get_results(mod_shannon_ref_active, shannon_ref_filtered, "Active")) %>%  mutate(Metrics = "Shannon index")
print(estimates_ref_shannon)
```

```{r}
# SIMPSON INDEX
res_simpson_ref_init <- rma.mv(yi = yi, V = build_cov_matrix(simpson_resvsref_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = simpson_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_simpson_ref <- get_outliers(res_simpson_init, simpson_resvsref_df)
simpson_ref_filtered <- remove_outliers(simpson_resvsref_df, outlier_simpson_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
simpson_ref_filtered$Restoration_strategy <- relevel(factor(simpson_ref_filtered$Restoration_strategy), ref = "Active")
mod_simpson_ref_active <- rma.mv(yi = yi, V = build_cov_matrix(simpson_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem +Prior_land_use + Restoration_time, random = ~ 1 | ID, data = simpson_ref_filtered)

### Passive as reference (Intercept = Passive)
simpson_ref_filtered$Restoration_strategy <- relevel(factor(simpson_ref_filtered$Restoration_strategy), ref = "Passive")
mod_simpson_ref_passive <- rma.mv(yi = yi,  V = build_cov_matrix(simpson_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = simpson_ref_filtered)

## REPORTING TABLE
estimates_ref_simpson <- rbind(
  get_results(mod_simpson_ref_passive, simpson_ref_filtered, "Passive"),  get_results(mod_simpson_ref_active, simpson_ref_filtered, "Active")) %>%  mutate(Metrics = "Simpson index")
print(estimates_ref_simpson)
```

#### Relative abundance

```{r}
# ASCOMYCOTA
## FIT MODEL
res_asco_ref_init <- rma.mv(yi = yi, V = build_cov_matrix(asco_resvsref_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = asco_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_asco_ref <- get_outliers(res_asco_init, asco_resvsref_df)
asco_ref_filtered <- remove_outliers(asco_resvsref_df, outlier_asco_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
asco_ref_filtered$Restoration_strategy <- relevel(factor(asco_ref_filtered$Restoration_strategy), ref = "Active")
mod_asco_ref_active <- rma.mv(yi = yi, V = build_cov_matrix(asco_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = asco_ref_filtered)

### Passive as reference (Intercept = Passive)
asco_ref_filtered$Restoration_strategy <- relevel(factor(asco_ref_filtered$Restoration_strategy), ref = "Passive")
mod_asco_ref_passive <- rma.mv(yi = yi, V = build_cov_matrix(asco_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = asco_ref_filtered)

## REPORTING TABLE
estimates_ref_asco <- rbind(get_results(mod_asco_ref_passive, asco_ref_filtered, "Passive"),  get_results(mod_asco_ref_active, asco_ref_filtered, "Active")) %>%  mutate(Metrics = "Ascomycota")
print(estimates_ref_asco)
```

```{r}
# BASIDIOMYCOTA
## FIT MODEL
res_basidio_ref_init <- rma.mv(yi = yi, V = build_cov_matrix(basidio_resvsref_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = basidio_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_basidio_ref <- get_outliers(res_basidio_init, basidio_resvsref_df)
basidio_ref_filtered <- remove_outliers(basidio_resvsref_df, outlier_basidio_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
basidio_ref_filtered$Restoration_strategy <- relevel(factor(basidio_ref_filtered$Restoration_strategy), ref = "Active")
mod_basidio_ref_active <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = basidio_ref_filtered)

### Passive as reference (Intercept = Passive)
basidio_ref_filtered$Restoration_strategy <- relevel(factor(basidio_ref_filtered$Restoration_strategy), ref = "Passive")
mod_basidio_ref_passive <- rma.mv(yi = yi, V = build_cov_matrix(basidio_ref_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID, data = basidio_ref_filtered)

## REPORTING TABLE
estimates_ref_basidio <- rbind(
  get_results(mod_basidio_ref_passive, basidio_ref_filtered, "Passive"),  get_results(mod_basidio_ref_active, basidio_ref_filtered, "Active")) %>%  mutate(Metrics = "Basidiomycota")
print(estimates_ref_basidio)
```

#### Community structure

```{r}
# BETA DIVERSITY
## FIT MODEL
res_beta_ref_init <- rma.mv(yi = yi, V = build_cov_matrix(beta_resvsref_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = beta_resvsref_df)

# REMOVE OUTLIERS IF ANY
outlier_beta_ref <- get_outliers(res_beta_init, beta_resvsref_df)
beta_ref_filtered <- remove_outliers(beta_resvsref_df, outlier_beta_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
beta_ref_filtered$Restoration_strategy <- relevel(factor(beta_ref_filtered$Restoration_strategy), ref = "Active")
mod_beta_ref_active <- rma.mv(yi = yi, V = build_cov_matrix(beta_ref_filtered, rho = 0.5),mods = ~ Restoration_strategy + Ecosystem +Prior_land_use + Restoration_time, random = ~ 1 | ID, data = beta_ref_filtered)

### Passive as reference (Intercept = Passive)
beta_ref_filtered$Restoration_strategy <- relevel(factor(beta_ref_filtered$Restoration_strategy), ref = "Passive")
mod_beta_ref_passive <- rma.mv(yi = yi, V = build_cov_matrix(beta_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = beta_ref_filtered)

## REPORTING TABLE
estimates_ref_beta <- rbind(get_results(mod_beta_ref_passive, beta_ref_filtered, "Passive"), get_results(mod_beta_ref_active, beta_ref_filtered, "Active")) %>%  mutate(Metrics = "Beta diversity")
print(estimates_ref_beta)
```

```{r}
# STRUCTURE 
## FIT MODEL
res_comp_ref_init <- rma.mv(yi = yi, V = build_cov_matrix(comp_resvsref_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = comp_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_comp_ref <- get_outliers(res_comp_init, comp_resvsref_df)
comp_ref_filtered <- remove_outliers(comp_resvsref_df, outlier_comp_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
comp_ref_filtered$Restoration_strategy <- relevel(factor(comp_ref_filtered$Restoration_strategy), ref = "Active")
mod_comp_ref_active <- rma.mv(yi = yi, V = build_cov_matrix(comp_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = comp_ref_filtered)

### Passive as reference (Intercept = Passive)
comp_ref_filtered$Restoration_strategy <- relevel(factor(comp_ref_filtered$Restoration_strategy), ref = "Passive")
mod_comp_ref_passive <- rma.mv(yi = yi, V = build_cov_matrix(comp_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = comp_ref_filtered)

## REPORTING TABLE
estimates_ref_comp <- rbind(
  get_results(mod_comp_ref_passive, comp_ref_filtered, "Passive"), get_results(mod_comp_ref_active, comp_ref_filtered, "Active")) %>%  mutate(Metrics = "Structure")
print(estimates_ref_comp)
```

#### Biomass

```{r}
# PLFA CONTENT
## FIT MODEL
res_plfa_ref_init <- rma.mv(yi = yi, V = build_cov_matrix(plfa_resvsref_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = plfa_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_plfa_ref <- get_outliers(res_plfa_init, plfa_resvsref_df)
plfa_ref_filtered <- remove_outliers(plfa_resvsref_df, outlier_plfa_ref)

## FINAL MODELS (Active vs Passive Strategy Effects)
### Active as reference (Intercept = Active)
plfa_ref_filtered$Restoration_strategy <- relevel(factor(plfa_ref_filtered$Restoration_strategy), ref = "Active")
mod_plfa_ref_active <- rma.mv(yi = yi, V = build_cov_matrix(plfa_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = plfa_ref_filtered)

### Passive as reference (Intercept = Passive)
plfa_ref_filtered$Restoration_strategy <- relevel(factor(plfa_ref_filtered$Restoration_strategy), ref = "Passive")
mod_plfa_ref_passive <- rma.mv(yi = yi, V = build_cov_matrix(plfa_ref_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, data = plfa_ref_filtered)

## REPORTING TABLE
estimates_ref_plfa <- rbind(get_results(mod_plfa_ref_passive, plfa_ref_filtered, "Passive"), get_results(mod_plfa_ref_active, plfa_ref_filtered, "Active")) %>%  mutate(Metrics = "PLFA Biomass")
print(estimates_ref_plfa)
```

```{r eval=FALSE}
strategy_resvsref_df <- rbind(estimates_ref_otu, estimates_ref_chao1, estimates_ref_shannon, estimates_ref_simpson, estimates_ref_asco, estimates_ref_basidio, estimates_ref_beta, estimates_ref_comp, estimates_ref_plfa)
print(strategy_resvsref_df)
```

```{r eval=FALSE}
write.csv(file = "data/figure_data/strategy_resvsref_df.csv", strategy_resvsref_df, row.names = FALSE )
```

#### Figure 4.2

```{r}
strategy_resvsref_df <- read.csv("data/figure_data/strategy_resvsref_df.csv", header = TRUE)
alpha_ref <- strategy_resvsref_df[1:8,]
relabun_ref         <- strategy_resvsref_df[9:12,]
comm_ref            <- strategy_resvsref_df[13:16,]
plfa_ref            <- strategy_resvsref_df[17:18,]

# FORMAT LABELS
# ADD LABELS
alpha_restoration_ref <- add_labels2(alpha_ref, rev(c("OTU richness", "Chao1 richness", "Shannon index", "Simpson index")))
relabund_restoration_ref <- add_labels2(relabun_ref, rev(c("Ascomycota", "Basidiomycota")))
comm_restoration_ref <- add_labels2(comm_ref, c("Structure", "Beta diversity"))
plfa_restoration_ref <- add_labels2(plfa_ref, c("PLFA content"))

## ALPHA DIVERSITY
label_df <- data.frame(label = c("OTU richness", "Chao1 richness", "Shannon index", "Simpson index"), y = c(4.45, 3.45, 2.45, 1.45),  x = -2 )
alpha_restoration_ref$Metrics <- factor(alpha_restoration_ref$Metrics,  levels = c("OTU richness", "Chao1 richness", "Shannon index", "Simpson index"))

alpha_diversity_ref_plot <- ggplot(alpha_restoration_ref, aes(x = Estimate, y = Metrics, color = Restoration_strategy)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.6), size = 3) + geom_errorbar(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.6)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.6), hjust = 1.2, size = 3.0, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.6), hjust = -0.15, size = 3.0, show.legend = FALSE) + geom_text(data = label_df, aes(x = x, y = y, label = label), color = "black", size = 3.5, inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Passive" = "darkgreen", "Active" = "maroon")) + labs(x = "lnRR (alpha diversity)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.4)))

# RELATIVE ABUNDANCE
label_df_rel <- data.frame(label = c("Ascomycota", "Basidiomycota"), y = c(2.45, 1.45), x = -2)
relabund_restoration_ref$Metrics <- factor(relabund_restoration_ref$Metrics,  levels = c("Basidiomycota", "Ascomycota"))

relabun_ref_plot <- ggplot(relabund_restoration_ref, aes(x = Estimate, y = Metrics, color = Restoration_strategy)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.6), size = 3) + geom_errorbar(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.6)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.6), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.6), hjust = -0.15, size = 3.2, show.legend = FALSE) + geom_text(data = label_df_rel, aes(x = x, y = y, label = label), color = "black", size = 3.5, inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Passive" = "darkgreen", "Active" = "maroon")) + labs(x = "lnRR (relative abundance)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.4)))

# COMPOSITION
label_df_comm <- data.frame(label = c("Structure", "Beta diversity"),  y = c(2.45, 1.45),  x = -2)
comm_restoration_ref$Metrics <- factor(comm_restoration_ref$Metrics,  levels = c("Beta diversity", "Structure"))

comm_ref_plot <- ggplot(comm_restoration_ref, aes(x = Estimate, y = Metrics, color = Restoration_strategy)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.6), size = 3) + geom_errorbar(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.6)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.6), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.6), hjust = -0.15, size = 3.2, show.legend = FALSE) + geom_text(data = label_df_comm, aes(x = x, y = y, label = label), color = "black", size = 3.5, inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Passive" = "darkgreen", "Active" = "maroon")) + labs(x = "lnRR (composition)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.4)))

# BIOMASS
label_df_plfa <- data.frame(label = c("PLFA content"),y = 1.45, x = -2)
plfa_restoration_ref_plot <- ggplot(plfa_restoration_ref, aes(x = Estimate, y = Metrics, color = Restoration_strategy)) + geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.2) + geom_point(position = position_dodge(width = 0.6), size = 3) + geom_errorbar(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, position = position_dodge(width = 0.6)) + geom_text(aes(x = ci.lb, label = lab_k), position = position_dodge(width = 0.6), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = lab_percent), position = position_dodge(width = 0.6), hjust = -0.15, size = 3.2, show.legend = FALSE) + geom_text(data = label_df_plfa, aes(x = x, y = y, label = label), color = "black", size = 3.5, inherit.aes = FALSE, hjust = 0) + scale_color_manual(values = c("Passive" = "darkgreen", "Active" = "maroon")) + labs(x = "lnRR (biomass)", y = NULL) + theme_pubr(border = TRUE, legend = "none") + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(size = 10)) + scale_x_continuous(expand = expansion(mult = c(0.04, 0.4)))
```

```{r}
Figure_4_ref_left <- ggarrange(alpha_diversity_ref_plot + theme(legend.position = "none"), plfa_restoration_ref_plot + theme(legend.position = "none"), ncol = 1, heights = c(1, 0.5), align = "v")
Figure_4_ref_right <- ggarrange(relabun_ref_plot + theme(legend.position = "none"), comm_ref_plot + theme(legend.position = "none"), ncol = 1, heights = c(1, 1), align = "v")
Figure_4_ref_final <- grid.arrange(Figure_4_ref_left, Figure_4_ref_right, ncol = 2, widths = c(1, 1), bottom = legend_bottom, top = textGrob("Restored vs Reference", gp = gpar(fontsize = 12, fontface = "bold")))
Figure_4.2 <- annotate_figure(Figure_4_ref_final, fig.lab = "(b)", fig.lab.pos = "top.right", fig.lab.face = "bold", fig.lab.size = 16)
```

```{r eval=FALSE}
ggsave("../Figure_4.2.tiff", plot = Figure_4.2, dpi = 600, height = 6, width = 5)
```

# Chapter IX: Effect of restoration time

## Restored vs Degraded

### Alpha diversity

```{r}
# OTU RICHNESS
## LOG TRANSFORM RESTORATION TIME
otu_resvsdeg_df$log_time <- log(otu_resvsdeg_df$Restoration_time)

## FIT MODEL
res_otu_mod <- rma.mv(yi ~ log_time * Ecosystem,V = build_cov_matrix(otu_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = otu_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_otu_deg <- get_outliers(res_otu_mod, otu_resvsdeg_df)
otu_deg_filtered <- remove_outliers(otu_resvsdeg_df, outlier_otu_deg)

## FINAL MODEL
res_otu_filtered <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(otu_deg_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = otu_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_otu_deg <- get_coefficient(res_otu_filtered)

## PREDICTION GRID
newdat_otu_deg <- expand.grid(log_time = seq(min(otu_deg_filtered$log_time, na.rm = TRUE), max(otu_deg_filtered$log_time, na.rm = TRUE),  length.out = 100), Ecosystem = levels(factor(otu_deg_filtered$Ecosystem)))

X_otu_deg <- model.matrix(~ log_time * Ecosystem, data = newdat_otu_deg)
pred_otu_deg <- predict(res_otu_filtered, newmods = X_otu_deg[, -1])

## PREDICTION DATASET
newdat_otu_deg <- cbind(newdat_otu_deg,  pred = pred_otu_deg$pred,  ci.lb = pred_otu_deg$ci.lb,  ci.ub = pred_otu_deg$ci.ub)

## PLOT
plot_otu_deg <- ggplot(newdat_otu_deg, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = otu_deg_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "OTU richness") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_otu_deg$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_otu_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_otu_deg)
```

```{r}
## LOG TRANSFORM RESTORATION TIME
chao1_resvsdeg_df$log_time <- log(chao1_resvsdeg_df$Restoration_time)

## FIT MODEL
res_chao1_mod <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(chao1_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = chao1_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_chao1_deg <- get_outliers(res_chao1_mod, chao1_resvsdeg_df)
chao1_deg_filtered <- remove_outliers(chao1_resvsdeg_df, outlier_chao1_deg)

## FINAL MODEL
res_chao1_filtered <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(chao1_deg_filtered, rho = 0.5),random = ~ 1 | ID,  method = "REML",  data = chao1_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_chao1_deg <- get_coefficient(res_chao1_filtered)

## PREDICTION GRID
newdat_chao1_deg <- expand.grid(log_time = seq(min(chao1_deg_filtered$log_time, na.rm = TRUE), max(chao1_deg_filtered$log_time, na.rm = TRUE), length.out = 100), Ecosystem = levels(factor(chao1_deg_filtered$Ecosystem)))
X_chao1_deg <- model.matrix(~ log_time * Ecosystem, data = newdat_chao1_deg)
pred_chao1_deg <- predict(res_chao1_filtered, newmods = X_chao1_deg[, -1])

## PREDICTION DATASET
newdat_chao1_deg <- cbind(newdat_chao1_deg,  pred = pred_chao1_deg$pred,  ci.lb = pred_chao1_deg$ci.lb,  ci.ub = pred_chao1_deg$ci.ub)

## PLOT
plot_chao1_deg <- ggplot(newdat_chao1_deg, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = chao1_deg_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Chao1 richness") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_chao1_deg$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_chao1_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_chao1_deg)
```

```{r}
# SHANNON INDEX
## LOG TRANSFORM RESTORATION TIME
shannon_resvsdeg_df$log_time <- log(shannon_resvsdeg_df$Restoration_time)

## FIT MODEL
res_shannon_mod <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(shannon_resvsdeg_df, rho = 0.5), random = ~ 1 | ID, method = "REML", data = shannon_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_shannon_deg <- get_outliers(res_shannon_mod, shannon_resvsdeg_df)
shannon_deg_filtered <- remove_outliers(shannon_resvsdeg_df, outlier_shannon_deg)

## FINAL MODEL
res_shannon_filtered <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(shannon_deg_filtered, rho = 0.5), random = ~ 1 | ID, method = "REML",data = shannon_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_shannon_deg <- get_coefficient(res_shannon_filtered)

## PREDCTION
newdat_shannon_deg <- expand.grid(log_time = seq(min(shannon_deg_filtered$log_time, na.rm = TRUE),max(shannon_deg_filtered$log_time, na.rm = TRUE), length.out = 100),Ecosystem =levels(factor(shannon_deg_filtered$Ecosystem)))
X_shannon <- model.matrix(~ log_time * Ecosystem, data = newdat_shannon_deg)
pred_shannon_deg <- predict(res_shannon_filtered, newmods = X_shannon[, -1])

## PREDICTION DATASET
newdat_shannon_deg <- cbind(newdat_shannon_deg, pred = pred_shannon_deg$pred, ci.lb = pred_shannon_deg$ci.lb, ci.ub = pred_shannon_deg$ci.ub)

## PLOT
plot_shannon_deg <- ggplot(newdat_shannon_deg, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = shannon_deg_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Shannon index") +  theme_pubr(border = TRUE, legend = "none") +   theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1)))+  annotate("text", x = -Inf, y = -Inf, label = coef_sig_shannon_deg$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +    annotate("text", x = -Inf, y = -Inf, label = coef_sig_shannon_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_shannon_deg)
```

```{r}
## LOG TRANSFORM RESTORATION TIME
simpson_resvsdeg_df$log_time <- log(simpson_resvsdeg_df$Restoration_time)

## FIT MODEL
res_simpson_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(simpson_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = simpson_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_simpson_deg <- get_outliers(res_simpson_mod, simpson_resvsdeg_df)
simpson_deg_filtered <- remove_outliers(simpson_resvsdeg_df, outlier_simpson_deg)

## FINAL MODEL
res_simpson_filtered <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(simpson_deg_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = simpson_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_simpson_deg <- get_coefficient(res_simpson_filtered)

## PREDICTION GRID
newdat_simpson_deg <- expand.grid(log_time = seq(min(simpson_deg_filtered$log_time, na.rm = TRUE),max(simpson_deg_filtered$log_time, na.rm = TRUE),length.out = 100), Ecosystem = levels(factor(simpson_deg_filtered$Ecosystem)))

X_simpson_deg <- model.matrix(~ log_time * Ecosystem, data = newdat_simpson_deg)
pred_simpson_deg <- predict(res_simpson_filtered, newmods = X_simpson_deg[, -1])

## PREDICTION DATASET
newdat_simpson_deg <- cbind(newdat_simpson_deg,  pred = pred_simpson_deg$pred,  ci.lb = pred_simpson_deg$ci.lb,  ci.ub = pred_simpson_deg$ci.ub)

## PLOT
plot_simpson_deg <- ggplot(newdat_simpson_deg, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = simpson_deg_filtered,    aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2  ) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Simpson index") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_simpson_deg$forest,  hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_simpson_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_simpson_deg)
```

### Relative abundance

```{r}
# ASCOMYCOTA
## LOG TRANSFORM RESTORATION TIME
asco_resvsdeg_df$log_time <- log(asco_resvsdeg_df$Restoration_time)

## FIT MODEL
res_asco_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(asco_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = asco_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_asco_deg <- get_outliers(res_asco_mod, asco_resvsdeg_df)
asco_deg_filtered <- remove_outliers(asco_resvsdeg_df, outlier_asco_deg)

## FINAL MODEL
res_asco_filtered <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(asco_deg_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = asco_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_asco_deg <- get_coefficient(res_asco_filtered)

## PREDICTION GRID
newdat_asco_deg <- expand.grid(log_time = seq(min(asco_deg_filtered$log_time, na.rm = TRUE),max(asco_deg_filtered$log_time, na.rm = TRUE),length.out = 100),Ecosystem = levels(factor(asco_deg_filtered$Ecosystem)))
X_asco_deg <- model.matrix(~ log_time * Ecosystem, data = newdat_asco_deg)
pred_asco_deg <- predict(res_asco_filtered, newmods = X_asco_deg[, -1])

## PREDICTION DATASET
newdat_asco_deg <- cbind(newdat_asco_deg,  pred = pred_asco_deg$pred,  ci.lb = pred_asco_deg$ci.lb,  ci.ub = pred_asco_deg$ci.ub)

## PLOT
plot_asco_deg <- ggplot(newdat_asco_deg, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = asco_deg_filtered,    aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2  ) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Ascomycota") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_asco_deg$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_asco_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_asco_deg)
```

```{r}
# BASIDIOMYCOTA
## LOG TRANSFORM RESTORATION TIME
basidio_resvsdeg_df$log_time <- log(basidio_resvsdeg_df$Restoration_time)

## FIT MODEL
res_basidio_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(basidio_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = basidio_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_basidio_deg <- get_outliers(res_basidio_mod, basidio_resvsdeg_df)
basidio_deg_filtered <- remove_outliers(basidio_resvsdeg_df, outlier_basidio_deg)

## FINAL MODEL
res_basidio_filtered <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(basidio_deg_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = basidio_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_basidio_deg <- get_coefficient(res_basidio_filtered)

## PREDICTION GRID
newdat_basidio_deg <- expand.grid(log_time = seq(min(basidio_deg_filtered$log_time, na.rm = TRUE),max(basidio_deg_filtered$log_time, na.rm = TRUE), length.out = 100),Ecosystem = levels(factor(basidio_deg_filtered$Ecosystem)))
X_basidio_deg <- model.matrix(~ log_time * Ecosystem, data = newdat_basidio_deg)
pred_basidio_deg <- predict(res_basidio_filtered, newmods = X_basidio_deg[, -1])

## PREDICTION DATASET
newdat_basidio_deg <- cbind(newdat_basidio_deg, pred = pred_basidio_deg$pred, ci.lb = pred_basidio_deg$ci.lb,  ci.ub = pred_basidio_deg$ci.ub)

## PLOT
plot_basidio_deg <- ggplot(newdat_basidio_deg, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = basidio_deg_filtered,    aes(x = log_time, y = yi, color = Ecosystem),    alpha = 0.4, size = 2 ) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Basidiomycota") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_basidio_deg$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_basidio_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_basidio_deg)
```

### Composition

```{r}
# BETA DIVERSITY
## LOG TRANSFORM RESTORATION TIME
beta_resvsdeg_df$log_time <- log(beta_resvsdeg_df$Restoration_time)

## FIT MODEL
res_beta_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(beta_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = beta_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_beta_deg <- get_outliers(res_beta_mod, beta_resvsdeg_df)
beta_deg_filtered <- remove_outliers(beta_resvsdeg_df, outlier_beta_deg)

## FINAL MODEL
res_beta_filtered <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(beta_deg_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = beta_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_beta_deg <- get_coefficient(res_beta_filtered)

## PREDICTION GRID
newdat_beta_deg <- expand.grid(log_time = seq(min(beta_deg_filtered$log_time, na.rm = TRUE),  max(beta_deg_filtered$log_time, na.rm = TRUE),  length.out = 100),Ecosystem = levels(factor(beta_deg_filtered$Ecosystem)))

X_beta_deg <- model.matrix(~ log_time * Ecosystem, data = newdat_beta_deg)
pred_beta_deg <- predict(res_beta_filtered, newmods = X_beta_deg[, -1])

## PREDICTION DATASET
newdat_beta_deg <- cbind( newdat_beta_deg,  pred = pred_beta_deg$pred,  ci.lb = pred_beta_deg$ci.lb,  ci.ub = pred_beta_deg$ci.ub)

## PLOT
plot_beta_deg <- ggplot(newdat_beta_deg, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = beta_deg_filtered,  aes(x = log_time, y = yi, color = Ecosystem),  alpha = 0.4, size = 2 ) + geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Beta diversity") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) + scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_beta_deg$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_beta_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_beta_deg)
```

```{r}
# STRUCTURE
## LOG TRANSFORM RESTORATION TIME
comp_resvsdeg_df$log_time <- log(comp_resvsdeg_df$Restoration_time)

## FIT MODEL
res_comp_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(comp_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = comp_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_comp_deg <- get_outliers(res_comp_mod, comp_resvsdeg_df)
comp_deg_filtered <- remove_outliers(comp_resvsdeg_df, outlier_comp_deg)

## FINAL MODEL
res_comp_filtered <- rma.mv(yi ~ log_time * Ecosystem,V = build_cov_matrix(comp_deg_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = comp_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_comp_deg <- get_coefficient(res_comp_filtered)

## PREDICTION GRID
newdat_comp_deg <- expand.grid(log_time = seq(min(comp_deg_filtered$log_time, na.rm = TRUE), max(comp_deg_filtered$log_time, na.rm = TRUE),length.out = 100),Ecosystem = levels(factor(comp_deg_filtered$Ecosystem)))

X_comp_deg <- model.matrix(~ log_time * Ecosystem, data = newdat_comp_deg)
pred_comp_deg <- predict(res_comp_filtered, newmods = X_comp_deg[, -1])

## PREDICTION DATASET
newdat_comp_deg <- cbind(newdat_comp_deg,  pred = pred_comp_deg$pred,  ci.lb = pred_comp_deg$ci.lb,  ci.ub = pred_comp_deg$ci.ub)

## PLOT
plot_comp_deg <- ggplot(newdat_comp_deg, aes(x = log_time, y = pred, color = Ecosystem)) + geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) + geom_point(data = comp_deg_filtered, aes(x = log_time, y = yi, color = Ecosystem),alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Structure") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_comp_deg$forest,  hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_comp_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_comp_deg)
```

### Biomass

```{r}
# PLFA CONTENT
## LOG TRANSFORM RESTORATION TIME
plfa_resvsdeg_df$log_time <- log(plfa_resvsdeg_df$Restoration_time)

## FIT MODEL
res_plfa_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(plfa_resvsdeg_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = plfa_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_plfa_deg <- get_outliers(res_plfa_mod, plfa_resvsdeg_df)
plfa_deg_filtered <- remove_outliers(plfa_resvsdeg_df, outlier_plfa_deg)

## FINAL MODEL
res_plfa_filtered <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(plfa_deg_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = plfa_deg_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_plfa_deg <- get_coefficient(res_plfa_filtered)

## PREDICTION GRID
newdat_plfa_deg <- expand.grid(log_time = seq(min(plfa_deg_filtered$log_time, na.rm = TRUE),max(plfa_deg_filtered$log_time, na.rm = TRUE),  length.out = 100),Ecosystem = levels(factor(plfa_deg_filtered$Ecosystem)))

X_plfa_deg <- model.matrix(~ log_time * Ecosystem, data = newdat_plfa_deg)
pred_plfa_deg <- predict(res_plfa_filtered, newmods = X_plfa_deg[, -1])

## PREDICTION DATASET
newdat_plfa_deg <- cbind(newdat_plfa_deg,  pred = pred_plfa_deg$pred,  ci.lb = pred_plfa_deg$ci.lb,  ci.ub = pred_plfa_deg$ci.ub)

## PLOT
plot_plfa_deg <- ggplot(newdat_plfa_deg, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point( data = plfa_deg_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2 ) + geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "PLFA content") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_plfa_deg$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_plfa_deg$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_plfa_deg)
```

### Figure 5.1

```{r}
# Update just the first plot's theme
plot_otu_deg <- plot_otu_deg + theme(legend.text = element_text(size = 14), legend.title = element_text(size = 15, face = "plain"))
final_deg_grid <- ggarrange(plot_otu_deg, plot_chao1_deg, plot_shannon_deg, plot_simpson_deg, plot_asco_deg, plot_basidio_deg, plot_beta_deg, plot_comp_deg, plot_plfa_deg, ncol = 3, nrow = 3, labels = NULL, common.legend = TRUE, legend = "bottom", align = "hv")
resvsdeg_restoration_time_plot <- annotate_figure(final_deg_grid, top = text_grob("Restored vs Degraded", face = "bold", size = 16, vjust = 0.5), left = text_grob("lnRR", color = "black", size = 16, rot = 90, vjust = 1.5), bottom = text_grob("log(restoration time)", color = "black", size = 16, vjust = -4), fig.lab = "(a)", fig.lab.pos = "top.right", fig.lab.face = "bold",fig.lab.size = 18)
```

```{r eval=FALSE}
ggsave("../Figure_5.1.jpg", plot = resvsdeg_restoration_time_plot, dpi = 800, height = 11, width = 9)
```

## Restored vs Reference

### Alpha diversity

```{r}
# OTU RICHNESS
## LOG TRANSFORM RESTORATION TIME
otu_resvsref_df$log_time <- log(otu_resvsref_df$Restoration_time)

## FIT MODEL
res_otu_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(otu_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = otu_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_otu_ref <- get_outliers(res_otu_mod, otu_resvsref_df)
otu_ref_filtered <- remove_outliers(otu_resvsref_df, outlier_otu_ref)

## FINAL MODEL
res_otu_filtered <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(otu_ref_filtered, rho = 0.5), random = ~ 1 | ID, method = "REML", data = otu_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_otu_ref <- get_coefficient(res_otu_filtered)

## PREDICTION GRID
newdat_otu_ref <- expand.grid(log_time = seq(min(otu_ref_filtered$log_time, na.rm = TRUE), max(otu_ref_filtered$log_time, na.rm = TRUE), length.out = 100),Ecosystem = levels(factor(otu_ref_filtered$Ecosystem))
)

X_otu_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_otu_ref)
pred_otu_ref <- predict(res_otu_filtered, newmods = X_otu_ref[, -1])

## PREDICTION DATASET
newdat_otu_ref <- cbind(newdat_otu_ref,  pred = pred_otu_ref$pred,  ci.lb = pred_otu_ref$ci.lb,  ci.ub = pred_otu_ref$ci.ub)

## PLOT
plot_otu_ref <- ggplot(newdat_otu_ref, aes(x = log_time, y = pred, color = Ecosystem)) + geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = otu_ref_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) + geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "OTU richness") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_otu_ref$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") + annotate("text", x = -Inf, y = -Inf, label = coef_sig_otu_ref$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_otu_ref)
```

```{r}
# CHAO1 RICHNESS
## LOG TRANSFORM RESTORATION TIME
chao1_resvsref_df$log_time <- log(chao1_resvsref_df$Restoration_time)

## FIT MODEL
res_chao1_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(chao1_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = chao1_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_chao1_ref <- get_outliers(res_chao1_mod, chao1_resvsref_df)
chao1_ref_filtered <- remove_outliers(chao1_resvsref_df, outlier_chao1_ref)

## FINAL MODEL
res_chao1_filtered <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(chao1_ref_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = chao1_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_chao1_ref <- get_coefficient(res_chao1_filtered)

## PREDICTION GRID
newdat_chao1_ref <- expand.grid(log_time = seq(min(chao1_ref_filtered$log_time, na.rm = TRUE), max(chao1_ref_filtered$log_time, na.rm = TRUE), length.out = 100), Ecosystem = levels(factor(chao1_ref_filtered$Ecosystem)))
X_chao1_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_chao1_ref)
pred_chao1_ref <- predict(res_chao1_filtered, newmods = X_chao1_ref[, -1])

## PREDICTION DATASET
newdat_chao1_ref <- cbind(newdat_chao1_ref,  pred = pred_chao1_ref$pred,  ci.lb = pred_chao1_ref$ci.lb,  ci.ub = pred_chao1_ref$ci.ub)

## PLOT
plot_chao1_ref <- ggplot(newdat_chao1_ref, aes(x = log_time, y = pred, color = Ecosystem)) +geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem),alpha = 0.2, color = NA) +  geom_point(data = chao1_ref_filtered,    aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) +geom_line(linewidth = 1.2) +scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Chao1 richness") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_chao1_ref$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_chao1_ref$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_chao1_ref)
```

```{r}
# SHANNON INDEX
## LOG TRANSFORM RESTORATION TIME
shannon_resvsref_df$log_time <- log(shannon_resvsref_df$Restoration_time)

## FIT MODEL
res_shannon_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(shannon_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = shannon_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_shannon_ref <- get_outliers(res_shannon_mod, shannon_resvsref_df)
shannon_ref_filtered <- remove_outliers(shannon_resvsref_df, outlier_shannon_ref)

## FINAL MODEL
res_shannon_filtered <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(shannon_ref_filtered, rho = 0.5),random = ~ 1 | ID,  method = "REML",  data = shannon_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_shannon_ref <- get_coefficient(res_shannon_filtered)

## PREDICTION GRID
newdat_shannon_ref <- expand.grid(log_time = seq(min(shannon_ref_filtered$log_time, na.rm = TRUE),max(shannon_ref_filtered$log_time, na.rm = TRUE), length.out = 100), Ecosystem = levels(factor(shannon_ref_filtered$Ecosystem)))
X_shannon_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_shannon_ref)
pred_shannon_ref <- predict(res_shannon_filtered, newmods = X_shannon_ref[, -1])

## PREDICTION DATASET
newdat_shannon_ref <- cbind(newdat_shannon_ref,  pred = pred_shannon_ref$pred,  ci.lb = pred_shannon_ref$ci.lb,  ci.ub = pred_shannon_ref$ci.ub)

## PLOT
plot_shannon_ref <- ggplot(newdat_shannon_ref, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem),alpha = 0.2, color = NA) +geom_point(data = shannon_ref_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) +geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Shannon index") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_shannon_ref$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_shannon_ref$grass,   hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_shannon_ref)
```

```{r}
# SIMPSON INDEX
## LOG TRANSFORM RESTORATION TIME
simpson_resvsref_df$log_time <- log(simpson_resvsref_df$Restoration_time)

## FIT MODEL
res_simpson_mod <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(simpson_resvsref_df, rho = 0.5), random = ~ 1 | ID, method = "REML", data = simpson_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_simpson_ref <- get_outliers(res_simpson_mod, simpson_resvsref_df)
simpson_ref_filtered <- remove_outliers(simpson_resvsref_df, outlier_simpson_ref)

## FINAL MODEL
res_simpson_filtered <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(simpson_ref_filtered, rho = 0.5), random = ~ 1 | ID, method = "REML", data = simpson_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_simpson_ref <- get_coefficient(res_simpson_filtered)

## PREDICTION GRID
newdat_simpson_ref <- expand.grid(log_time = seq(min(simpson_ref_filtered$log_time, na.rm = TRUE), max(simpson_ref_filtered$log_time, na.rm = TRUE), length.out = 100), Ecosystem = levels(factor(simpson_ref_filtered$Ecosystem)))
X_simpson_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_simpson_ref)
pred_simpson_ref <- predict(res_simpson_filtered, newmods = X_simpson_ref[, -1])

## PREDICTION DATASET
newdat_simpson_ref <- cbind(  newdat_simpson_ref,  pred = pred_simpson_ref$pred,  ci.lb = pred_simpson_ref$ci.lb,  ci.ub = pred_simpson_ref$ci.ub)

## PLOT
plot_simpson_ref <- ggplot(newdat_simpson_ref, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = simpson_ref_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Simpson index") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_simpson_ref$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") + annotate("text", x = -Inf, y = -Inf, label = coef_sig_simpson_ref$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_simpson_ref)
```

### Relative abundance

```{r}
# ASCOMYCOTA
## LOG TRANSFORM RESTORATION TIME
asco_resvsref_df$log_time <- log(asco_resvsref_df$Restoration_time)

## FIT MODEL
res_asco_mod <- rma.mv(  yi ~ log_time * Ecosystem,  V = build_cov_matrix(asco_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = asco_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_asco_ref <- get_outliers(res_asco_mod, asco_resvsref_df)
asco_ref_filtered <- remove_outliers(asco_resvsref_df, outlier_asco_ref)

## FINAL MODEL
res_asco_filtered <- rma.mv(  yi ~ log_time * Ecosystem,  V = build_cov_matrix(asco_ref_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = asco_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_asco_ref <- get_coefficient(res_asco_filtered)

## PREDICTION GRID
newdat_asco_ref <- expand.grid(log_time = seq(min(asco_ref_filtered$log_time, na.rm = TRUE), max(asco_ref_filtered$log_time, na.rm = TRUE), length.out = 100), Ecosystem = levels(factor(asco_ref_filtered$Ecosystem)))
X_asco_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_asco_ref)
pred_asco_ref <- predict(res_asco_filtered, newmods = X_asco_ref[, -1])

## PREDICTION DATASET
newdat_asco_ref <- cbind(  newdat_asco_ref,  pred = pred_asco_ref$pred,  ci.lb = pred_asco_ref$ci.lb,  ci.ub = pred_asco_ref$ci.ub)

## PLOT
plot_asco_ref <- ggplot(newdat_asco_ref, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = asco_ref_filtered, aes(x = log_time, y = yi, color = Ecosystem),  alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Ascomycota") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_asco_ref$forest,   hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_asco_ref$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_asco_ref)
```

```{r}
# BASIDIOMYCOTA
## LOG TRANSFORM RESTORATION TIME
basidio_resvsref_df$log_time <- log(basidio_resvsref_df$Restoration_time)

## FIT MODEL
res_basidio_mod <- rma.mv(yi ~ log_time * Ecosystem,  V = build_cov_matrix(basidio_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = basidio_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_basidio_ref <- get_outliers(res_basidio_mod, basidio_resvsref_df)
basidio_ref_filtered <- remove_outliers(basidio_resvsref_df, outlier_basidio_ref)

## FINAL MODEL
res_basidio_filtered <- rma.mv( yi ~ log_time * Ecosystem, V = build_cov_matrix(basidio_ref_filtered, rho = 0.5), random = ~ 1 | ID, method = "REML", data = basidio_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_basidio_ref <- get_coefficient(res_basidio_filtered)

## PREDICTION GRID
newdat_basidio_ref <- expand.grid(log_time = seq(min(basidio_ref_filtered$log_time, na.rm = TRUE), max(basidio_ref_filtered$log_time, na.rm = TRUE), length.out = 100),  Ecosystem = levels(factor(basidio_ref_filtered$Ecosystem)))
X_basidio_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_basidio_ref)
pred_basidio_ref <- predict(res_basidio_filtered, newmods = X_basidio_ref[, -1])

## PREDICTION DATASET
newdat_basidio_ref <- cbind(  newdat_basidio_ref,  pred = pred_basidio_ref$pred,  ci.lb = pred_basidio_ref$ci.lb,  ci.ub = pred_basidio_ref$ci.ub)

## PLOT
plot_basidio_ref <- ggplot(newdat_basidio_ref, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem),alpha = 0.2, color = NA) +geom_point(data = basidio_ref_filtered, aes(x = log_time, y = yi, color = Ecosystem),alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Basidiomycota") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_basidio_ref$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_basidio_ref$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_basidio_ref)
```

### Composition

```{r}
# BETA DIVERSITY
## LOG TRANSFORM RESTORATION TIME
beta_resvsref_df$log_time <- log(beta_resvsref_df$Restoration_time)

## FIT MODEL
res_beta_mod <- rma.mv(  yi ~ log_time * Ecosystem,  V = build_cov_matrix(beta_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = beta_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_beta_ref <- get_outliers(res_beta_mod, beta_resvsref_df)
beta_ref_filtered <- remove_outliers(beta_resvsref_df, outlier_beta_ref)

## FINAL MODEL
res_beta_filtered <- rma.mv(yi ~ log_time * Ecosystem, V = build_cov_matrix(beta_ref_filtered, rho = 0.5), random = ~ 1 | ID,  method = "REML",  data = beta_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_beta_ref <- get_coefficient(res_beta_filtered)

## PREDICTION GRID
newdat_beta_ref <- expand.grid(log_time = seq(min(beta_ref_filtered$log_time, na.rm = TRUE), max(beta_ref_filtered$log_time, na.rm = TRUE), length.out = 100 ),  Ecosystem = levels(factor(beta_ref_filtered$Ecosystem)))
X_beta_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_beta_ref)
pred_beta_ref <- predict(res_beta_filtered, newmods = X_beta_ref[, -1])

## PREDICTION DATASET
newdat_beta_ref <- cbind(  newdat_beta_ref,  pred = pred_beta_ref$pred,  ci.lb = pred_beta_ref$ci.lb,  ci.ub = pred_beta_ref$ci.ub)

## PLOT
plot_beta_ref <- ggplot(newdat_beta_ref, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = beta_ref_filtered,aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Beta diversity") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_beta_ref$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_beta_ref$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_beta_ref)
```

```{r}
# STRUCTURE
## LOG TRANSFORM RESTORATION TIME
comp_resvsref_df$log_time <- log(comp_resvsref_df$Restoration_time)

## FIT MODEL
res_comp_mod <- rma.mv(  yi ~ log_time * Ecosystem,  V = build_cov_matrix(comp_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = comp_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_comp_ref <- get_outliers(res_comp_mod, comp_resvsref_df)
comp_ref_filtered <- remove_outliers(comp_resvsref_df, outlier_comp_ref)

## FINAL MODEL
res_comp_filtered <- rma.mv(  yi ~ log_time * Ecosystem,  V = build_cov_matrix(comp_ref_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = comp_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_comp_ref <- get_coefficient(res_comp_filtered)

## PREDICTION GRID
newdat_comp_ref <- expand.grid(log_time = seq(min(comp_ref_filtered$log_time, na.rm = TRUE), max(comp_ref_filtered$log_time, na.rm = TRUE), length.out = 100  ), Ecosystem = levels(factor(comp_ref_filtered$Ecosystem)))
X_comp_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_comp_ref)
pred_comp_ref <- predict(res_comp_filtered, newmods = X_comp_ref[, -1])

## PREDICTION DATASET
newdat_comp_ref <- cbind(  newdat_comp_ref,  pred = pred_comp_ref$pred,  ci.lb = pred_comp_ref$ci.lb,  ci.ub = pred_comp_ref$ci.ub)

## PLOT
plot_comp_ref <- ggplot(newdat_comp_ref, aes(x = log_time, y = pred, color = Ecosystem)) +  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) +  geom_point(data = comp_ref_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) +  geom_line(linewidth = 1.2) +  scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) +  labs(x = "", y = "", title = "Structure") +  theme_pubr(border = TRUE, legend = "none") +  theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) +  scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_comp_ref$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") +  annotate("text", x = -Inf, y = -Inf, label = coef_sig_comp_ref$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_comp_ref)
```

### Biomass

```{r}
# PLFA CONTENT
## LOG TRANSFORM RESTORATION TIME
plfa_resvsref_df$log_time <- log(plfa_resvsref_df$Restoration_time)

## FIT MODEL
res_plfa_mod <- rma.mv(  yi ~ log_time * Ecosystem,  V = build_cov_matrix(plfa_resvsref_df, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = plfa_resvsref_df)

## REMOVE OUTLIERS IF ANY
outlier_plfa_ref <- get_outliers(res_plfa_mod, plfa_resvsref_df)
plfa_ref_filtered <- remove_outliers(plfa_resvsref_df, outlier_plfa_ref)

## FINAL MODEL
res_plfa_filtered <- rma.mv(  yi ~ log_time * Ecosystem,  V = build_cov_matrix(plfa_ref_filtered, rho = 0.5),  random = ~ 1 | ID,  method = "REML",  data = plfa_ref_filtered)

## GET COEFFICIENTS AND SIGNIFICANCE
coef_sig_plfa_ref <- get_coefficient(res_plfa_filtered)

## PREDICTION GRID
newdat_plfa_ref <- expand.grid( log_time = seq( min(plfa_ref_filtered$log_time, na.rm = TRUE),max(plfa_ref_filtered$log_time, na.rm = TRUE),    length.out = 100  ),  Ecosystem = levels(factor(plfa_ref_filtered$Ecosystem)))
X_plfa_ref <- model.matrix(~ log_time * Ecosystem, data = newdat_plfa_ref)
pred_plfa_ref <- predict(res_plfa_filtered, newmods = X_plfa_ref[, -1])

## PREDICTION DATASET
newdat_plfa_ref <- cbind(  newdat_plfa_ref,  pred = pred_plfa_ref$pred,  ci.lb = pred_plfa_ref$ci.lb,  ci.ub = pred_plfa_ref$ci.ub)

## PLOT
plot_plfa_ref <- ggplot(newdat_plfa_ref, aes(x = log_time, y = pred, color = Ecosystem)) + geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub, fill = Ecosystem), alpha = 0.2, color = NA) + geom_point(data = plfa_ref_filtered, aes(x = log_time, y = yi, color = Ecosystem), alpha = 0.4, size = 2) + geom_line(linewidth = 1.2) + scale_color_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + scale_fill_manual(values = c("Forest" = "black", "Grassland" = "chocolate")) + labs(x = "", y = "", title = "PLFA content") + theme_pubr(border = TRUE, legend = "none") + theme(plot.title = element_text(hjust = 0.5, vjust = -0.5)) + scale_y_continuous(expand = expansion(mult = c(0.3, 0.1))) + annotate("text", x = -Inf, y = -Inf, label = coef_sig_plfa_ref$forest, hjust = -0.05, vjust = -2.5, size = 3.5, color = "black") + annotate("text", x = -Inf, y = -Inf, label = coef_sig_plfa_ref$grass, hjust = -0.05, vjust = -1.0, size = 3.5, color = "chocolate")
print(plot_plfa_ref)
```

### Figure 5.2

```{r}
plot_otu_ref <- plot_otu_ref +  theme(legend.text = element_text(size = 14), legend.title = element_text(size = 15, face = "plain"))
final_ref_grid <- ggarrange(plot_otu_ref, plot_chao1_ref, plot_shannon_ref, plot_simpson_ref, plot_asco_ref, plot_basidio_ref,  plot_beta_ref, plot_comp_ref, plot_plfa_ref, ncol = 3, nrow = 3, labels = NULL, common.legend = TRUE,  legend = "bottom", align = "hv")
resvsref_restoration_time_plot <- annotate_figure(final_ref_grid,  top = text_grob("Restored vs Reference",  face = "bold", size = 16, vjust = 0.5),  left = text_grob("lnRR",  color = "black", size = 16, rot = 90, vjust = 1.5), bottom = text_grob("log(restoration time)", color = "black", size = 16, vjust = -4),  fig.lab = "(b)",   fig.lab.pos = "top.right",  fig.lab.face = "bold",  fig.lab.size = 18)
```

```{r eval=FALSE}
ggsave("../Figure_5.2.jpg", plot = resvsref_restoration_time_plot, dpi = 800, height = 11, width = 9)
```

# Chapter X: Test of ordination method

```{r}
# Read and prepare data
beta_resvsdeg_df <- read.csv("data/original_data/ord_test_resvsdeg.csv", header = TRUE) %>%  mutate(across(c(ID, Method, Restoration_strategy, Ecosystem, Prior_land_use), as.factor), Restoration_time = as.numeric(Restoration_time),         ControlID = paste(ID, Degraded_Mean, Degraded_SD, Degraded_SS, sep = "_")) %>%  mutate(ControlID = as.character(ControlID))

# Compute effect sizes (log response ratio)
beta_resvsdeg_df <- escalc(measure = "ROM",  n1i = Restored_SS, n2i = Degraded_SS, m1i = Restored_Mean, m2i = Degraded_Mean, sd1i = Restored_SD, sd2i = Degraded_SD, data = beta_resvsdeg_df)
res_method_beta_deg <- rma.mv(yi = yi,  V = build_cov_matrix(beta_resvsdeg_df, rho = 0.5),  mods = ~ Method, random = ~ 1 | ID, method = "REML", data = beta_resvsdeg_df)
summary(res_method_beta_deg)
anova(res_method_beta_deg)

sensitivity_df <- beta_resvsdeg_df %>%  filter(!Method %in% c("Non-metric", "Unimodal"))
V_beta_sens <- build_cov_matrix(sensitivity_df, rho = 0.5)
res_method_beta_sens <- rma.mv(yi = yi,  V = V_beta_sens, mods = ~ Method, random = ~ 1 | ID, method = "REML", data = sensitivity_df)
summary(res_method_beta_sens)
anova(res_method_beta_sens)
```

# Prior land use (Fig S4)

```{r}
table(otu_resvsdeg_df$Prior_land_use)
res_otu_init <- rma.mv(yi = yi, V = build_cov_matrix(otu_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = otu_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_otu_deg <- get_outliers(res_otu_init, otu_resvsdeg_df)
otu_filtered <- remove_outliers(otu_resvsdeg_df, outlier_otu_deg)

otu_filtered$Prior_land_use <- relevel(factor(otu_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi, V = build_cov_matrix(otu_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem +  Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = otu_filtered)

otu_filtered$Prior_land_use <- relevel(factor(otu_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi, V = build_cov_matrix(otu_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = otu_filtered)

otu_filtered$Prior_land_use <- relevel(factor(otu_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi, V = build_cov_matrix(otu_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID, method = "REML", data = otu_filtered)

otu_filtered$Prior_land_use <- relevel(factor(otu_filtered$Prior_land_use), ref = "Monoculture plantation")
res_mon <- rma.mv(yi = yi, V = build_cov_matrix(otu_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML", data = otu_filtered)


otu_filtered$Prior_land_use <- relevel(factor(otu_filtered$Prior_land_use), ref = "Pasture")
res_pat <- rma.mv(yi = yi, V = build_cov_matrix(otu_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID, method = "REML",  data = otu_filtered)

## REPORTING TABLE
estimates_df_otu <- rbind(get_results_prior_land_use(res_agri, otu_filtered, "Agriculture"),  get_results_prior_land_use(res_defor, otu_filtered, "Deforestation"), get_results_prior_land_use(res_min, otu_filtered, "Mining"), get_results_prior_land_use(res_mon, otu_filtered, "Monoculture plantation"), get_results_prior_land_use(res_pat, otu_filtered, "Pasture")) %>%  mutate(Metrics = "OTU richness")
print(estimates_df_otu)
```

```{r}
table(chao1_resvsdeg_df$Prior_land_use)
res_chao1_init <- rma.mv( yi = yi,  V = build_cov_matrix(chao1_resvsdeg_df, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML", data = chao1_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_chao1_deg <- get_outliers(res_chao1_init, chao1_resvsdeg_df)
chao1_filtered <- remove_outliers(chao1_resvsdeg_df, outlier_chao1_deg)

chao1_filtered$Prior_land_use <- relevel(factor(chao1_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi, V = build_cov_matrix(chao1_filtered, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = chao1_filtered)

chao1_filtered$Prior_land_use <- relevel(factor(chao1_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi,  V = build_cov_matrix(chao1_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = chao1_filtered)

chao1_filtered$Prior_land_use <- relevel(factor(chao1_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi,  V = build_cov_matrix(chao1_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = chao1_filtered)

chao1_filtered$Prior_land_use <- relevel(factor(chao1_filtered$Prior_land_use), ref = "Monoculture plantation")
res_mon <- rma.mv(yi = yi,  V = build_cov_matrix(chao1_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = chao1_filtered)

chao1_filtered$Prior_land_use <- relevel(factor(chao1_filtered$Prior_land_use), ref = "Pasture")
res_pat <- rma.mv(yi = yi,  V = build_cov_matrix(chao1_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = chao1_filtered)

chao1_filtered$Prior_land_use <- relevel(factor(chao1_filtered$Prior_land_use), ref = "Erosion")

res_ero <- rma.mv(yi = yi,  V = build_cov_matrix(chao1_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = chao1_filtered)

## REPORTING TABLE
estimates_df_chao1 <- rbind(get_results_prior_land_use(res_agri, chao1_filtered, "Agriculture"), get_results_prior_land_use(res_defor, chao1_filtered, "Deforestation"), get_results_prior_land_use(res_min, chao1_filtered, "Mining"),  get_results_prior_land_use(res_mon, chao1_filtered, "Monoculture plantation"),  get_results_prior_land_use(res_pat, chao1_filtered, "Pasture"), get_results_prior_land_use(res_ero, chao1_filtered, "Erosion")) %>%  mutate(Metrics = "Chao1 richness")
print(estimates_df_chao1)
```

```{r}
table(shannon_resvsdeg_df$Prior_land_use)
res_shannon_init <- rma.mv( yi = yi,  V = build_cov_matrix(shannon_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = shannon_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_shannon_deg <- get_outliers(res_shannon_init, shannon_resvsdeg_df)
shannon_filtered <- remove_outliers(shannon_resvsdeg_df, outlier_shannon_deg)

shannon_filtered$Prior_land_use <- relevel(factor(shannon_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi,  V = build_cov_matrix(shannon_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = shannon_filtered)

shannon_filtered$Prior_land_use <- relevel(factor(shannon_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi,  V = build_cov_matrix(shannon_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = shannon_filtered)

shannon_filtered$Prior_land_use <- relevel(factor(shannon_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi,  V = build_cov_matrix(shannon_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = shannon_filtered)

shannon_filtered$Prior_land_use <- relevel(factor(shannon_filtered$Prior_land_use), ref = "Monoculture plantation")
res_mon <- rma.mv(yi = yi,  V = build_cov_matrix(shannon_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = shannon_filtered)

shannon_filtered$Prior_land_use <- relevel(factor(shannon_filtered$Prior_land_use), ref = "Pasture")
res_pat <- rma.mv(yi = yi,  V = build_cov_matrix(shannon_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = shannon_filtered)

shannon_filtered$Prior_land_use <- relevel(factor(shannon_filtered$Prior_land_use), ref = "Erosion")
res_ero <- rma.mv(yi = yi,  V = build_cov_matrix(shannon_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = shannon_filtered)

## REPORTING TABLE
estimates_df_shannon <- rbind(get_results_prior_land_use(res_agri, shannon_filtered, "Agriculture"),  get_results_prior_land_use(res_defor, shannon_filtered, "Deforestation"), get_results_prior_land_use(res_min, shannon_filtered, "Mining"), get_results_prior_land_use(res_mon, shannon_filtered, "Monoculture plantation"), get_results_prior_land_use(res_pat, shannon_filtered, "Pasture"), get_results_prior_land_use(res_ero, shannon_filtered, "Erosion")) %>%  mutate(Metrics = "Shannon index")
print(estimates_df_shannon)
```

```{r}
table(simpson_resvsdeg_df$Prior_land_use)
res_simpson_init <- rma.mv(yi = yi,  V = build_cov_matrix(simpson_resvsdeg_df, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = simpson_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_simpson_deg <- get_outliers(res_simpson_init, simpson_resvsdeg_df)
simpson_filtered <- remove_outliers(simpson_resvsdeg_df, outlier_simpson_deg)

simpson_filtered$Prior_land_use <- relevel(factor(simpson_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi,  V = build_cov_matrix(simpson_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = simpson_filtered)

simpson_filtered$Prior_land_use <- relevel(factor(simpson_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi,  V = build_cov_matrix(simpson_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = simpson_filtered)

simpson_filtered$Prior_land_use <- relevel(factor(simpson_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi, V = build_cov_matrix(simpson_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = simpson_filtered)

simpson_filtered$Prior_land_use <- relevel(factor(simpson_filtered$Prior_land_use), ref = "Pasture")
res_pat <- rma.mv(yi = yi,  V = build_cov_matrix(simpson_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = simpson_filtered)

## REPORTING TABLE
estimates_df_simpson <- rbind(get_results_prior_land_use(res_agri, simpson_filtered, "Agriculture"),  get_results_prior_land_use(res_defor, simpson_filtered, "Deforestation"), get_results_prior_land_use(res_min, simpson_filtered, "Mining"), get_results_prior_land_use(res_pat, simpson_filtered, "Pasture")) %>%  mutate(Metrics = "Simpson index")
print(estimates_df_simpson)
```

```{r}
table(asco_resvsdeg_df$Prior_land_use)
res_asco_init <- rma.mv(yi = yi,  V = build_cov_matrix(asco_resvsdeg_df, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = asco_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_asco_deg <- get_outliers(res_asco_init, asco_resvsdeg_df)
asco_filtered <- remove_outliers(asco_resvsdeg_df, outlier_asco_deg)

asco_filtered$Prior_land_use <- relevel(factor(asco_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi,  V = build_cov_matrix(asco_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = asco_filtered)

asco_filtered$Prior_land_use <- relevel(factor(asco_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi,  V = build_cov_matrix(asco_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = asco_filtered)


asco_filtered$Prior_land_use <- relevel(factor(asco_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi,  V = build_cov_matrix(asco_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = asco_filtered)

asco_filtered$Prior_land_use <- relevel(factor(asco_filtered$Prior_land_use), ref = "Monoculture plantation")
res_mon <- rma.mv(yi = yi,  V = build_cov_matrix(asco_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = asco_filtered)

asco_filtered$Prior_land_use <- relevel(factor(asco_filtered$Prior_land_use), ref = "Pasture")
res_pat <- rma.mv(yi = yi,  V = build_cov_matrix(asco_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = asco_filtered)

asco_filtered$Prior_land_use <- relevel(factor(asco_filtered$Prior_land_use), ref = "Erosion")
res_ero <- rma.mv(yi = yi,  V = build_cov_matrix(asco_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = asco_filtered)

## REPORTING TABLE
estimates_df_asco <- rbind(get_results_prior_land_use(res_agri, asco_filtered, "Agriculture"), get_results_prior_land_use(res_defor, asco_filtered, "Deforestation"), get_results_prior_land_use(res_min, asco_filtered, "Mining"), get_results_prior_land_use(res_mon, asco_filtered, "Monoculture plantation"), get_results_prior_land_use(res_pat, asco_filtered, "Pasture"), get_results_prior_land_use(res_ero, asco_filtered, "Erosion")) %>%  mutate(Metrics = "Ascomycota")
print(estimates_df_asco)
```

```{r}
table(basidio_resvsdeg_df$Prior_land_use)
res_basidio_init <- rma.mv(yi = yi, V = build_cov_matrix(basidio_resvsdeg_df, rho = 0.5), mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time, random = ~ 1 | ID,  method = "REML",  data = basidio_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_basidio_deg <- get_outliers(res_basidio_init, basidio_resvsdeg_df)
basidio_filtered <- remove_outliers(basidio_resvsdeg_df, outlier_basidio_deg)

basidio_filtered$Prior_land_use <- relevel(factor(basidio_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = basidio_filtered)

basidio_filtered$Prior_land_use <- relevel(factor(basidio_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = basidio_filtered)

basidio_filtered$Prior_land_use <- relevel(factor(basidio_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = basidio_filtered)

basidio_filtered$Prior_land_use <- relevel(factor(basidio_filtered$Prior_land_use), ref = "Monoculture plantation")
res_mon <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = basidio_filtered)

basidio_filtered$Prior_land_use <- relevel(factor(basidio_filtered$Prior_land_use), ref = "Pasture")
res_pat <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = basidio_filtered)

basidio_filtered$Prior_land_use <- relevel(factor(basidio_filtered$Prior_land_use), ref = "Erosion")
res_ero <- rma.mv(yi = yi,  V = build_cov_matrix(basidio_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = basidio_filtered)

## REPORTING TABLE
estimates_df_basidio <- rbind(get_results_prior_land_use(res_agri, basidio_filtered, "Agriculture"),  get_results_prior_land_use(res_defor, basidio_filtered, "Deforestation"),  get_results_prior_land_use(res_min, basidio_filtered, "Mining"), get_results_prior_land_use(res_mon, basidio_filtered, "Monoculture plantation"), get_results_prior_land_use(res_pat, basidio_filtered, "Pasture"), get_results_prior_land_use(res_ero, basidio_filtered, "Erosion")) %>%  mutate(Metrics = "Basidiomycota")
print(estimates_df_basidio)
```

```{r}
table(beta_resvsdeg_df$Prior_land_use)
res_beta_init <- rma.mv(yi = yi,  V = build_cov_matrix(beta_resvsdeg_df, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = beta_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_beta_deg <- get_outliers(res_beta_init, beta_resvsdeg_df)
beta_filtered <- remove_outliers(beta_resvsdeg_df, outlier_beta_deg)

beta_filtered$Prior_land_use <- relevel(factor(beta_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi,  V = build_cov_matrix(beta_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = beta_filtered)

beta_filtered$Prior_land_use <- relevel(factor(beta_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi,  V = build_cov_matrix(beta_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = beta_filtered)

beta_filtered$Prior_land_use <- relevel(factor(beta_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi,  V = build_cov_matrix(beta_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = beta_filtered)

beta_filtered$Prior_land_use <- relevel(factor(beta_filtered$Prior_land_use), ref = "Monoculture plantation")
res_mon <- rma.mv(yi = yi,  V = build_cov_matrix(beta_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = beta_filtered)


beta_filtered$Prior_land_use <- relevel(factor(beta_filtered$Prior_land_use), ref = "Pasture")
res_pat <- rma.mv(yi = yi,  V = build_cov_matrix(beta_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = beta_filtered)

beta_filtered$Prior_land_use <- relevel(factor(beta_filtered$Prior_land_use), ref = "Erosion")
res_ero <- rma.mv(yi = yi,  V = build_cov_matrix(beta_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = beta_filtered)

## REPORTING TABLE
estimates_df_beta <- rbind(get_results_prior_land_use(res_agri, beta_filtered, "Agriculture"),  get_results_prior_land_use(res_defor, beta_filtered, "Deforestation"),  get_results_prior_land_use(res_min, beta_filtered, "Mining"),  get_results_prior_land_use(res_mon, beta_filtered, "Monoculture plantation"),  get_results_prior_land_use(res_pat, beta_filtered, "Pasture"), get_results_prior_land_use(res_ero, beta_filtered, "Erosion")) %>%  mutate(Metrics = "Beta diversity")
print(estimates_df_beta)
```

```{r}
table(comp_resvsdeg_df$Prior_land_use)
res_comp_init <- rma.mv(yi = yi,  V = build_cov_matrix(comp_resvsdeg_df, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = comp_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_comp_deg <- get_outliers(res_comp_init, comp_resvsdeg_df)
comp_filtered <- remove_outliers(comp_resvsdeg_df, outlier_comp_deg)

comp_filtered$Prior_land_use <- relevel(factor(comp_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi,  V = build_cov_matrix(comp_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = comp_filtered)

comp_filtered$Prior_land_use <- relevel(factor(comp_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi,  V = build_cov_matrix(comp_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = comp_filtered)

comp_filtered$Prior_land_use <- relevel(factor(comp_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi,  V = build_cov_matrix(comp_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = comp_filtered)

comp_filtered$Prior_land_use <- relevel(factor(comp_filtered$Prior_land_use), ref = "Monoculture plantation")
res_mon <- rma.mv(yi = yi,  V = build_cov_matrix(comp_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = comp_filtered)

comp_filtered$Prior_land_use <- relevel(factor(comp_filtered$Prior_land_use), ref = "Pasture")
res_pat <- rma.mv(yi = yi,  V = build_cov_matrix(comp_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = comp_filtered)

comp_filtered$Prior_land_use <- relevel(factor(comp_filtered$Prior_land_use), ref = "Erosion")
res_ero <- rma.mv(yi = yi,  V = build_cov_matrix(comp_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = comp_filtered)

## REPORTING TABLE
estimates_df_comp <- rbind(get_results_prior_land_use(res_agri, comp_filtered, "Agriculture"),  get_results_prior_land_use(res_defor, comp_filtered, "Deforestation"),  get_results_prior_land_use(res_min, comp_filtered, "Mining"),  get_results_prior_land_use(res_mon, comp_filtered, "Monoculture plantation"),  get_results_prior_land_use(res_pat, comp_filtered, "Pasture"), get_results_prior_land_use(res_ero, comp_filtered, "Erosion")) %>%  mutate(Metrics = "Community structure")
print(estimates_df_comp)
```

```{r}
table(plfa_resvsdeg_df$Prior_land_use)
res_plfa_init <- rma.mv(yi = yi,  V = build_cov_matrix(plfa_resvsdeg_df, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = plfa_resvsdeg_df)

## REMOVE OUTLIERS IF ANY
outlier_plfa_deg <- get_outliers(res_plfa_init, plfa_resvsdeg_df)
plfa_filtered <- remove_outliers(plfa_resvsdeg_df, outlier_plfa_deg)

plfa_filtered$Prior_land_use <- relevel(factor(plfa_filtered$Prior_land_use), ref = "Agriculture")
res_agri <- rma.mv(yi = yi,  V = build_cov_matrix(plfa_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = plfa_filtered)

plfa_filtered$Prior_land_use <- relevel(factor(plfa_filtered$Prior_land_use), ref = "Deforestation")
res_defor <- rma.mv(yi = yi,  V = build_cov_matrix(plfa_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = plfa_filtered)

plfa_filtered$Prior_land_use <- relevel(factor(plfa_filtered$Prior_land_use), ref = "Mining")
res_min <- rma.mv(yi = yi,  V = build_cov_matrix(plfa_filtered, rho = 0.5),  mods = ~ Restoration_strategy + Ecosystem + Prior_land_use + Restoration_time,  random = ~ 1 | ID,  method = "REML",  data = plfa_filtered)

## REPORTING TABLE
estimates_df_plfa <- rbind(get_results_prior_land_use(res_agri, plfa_filtered, "Agriculture"),  get_results_prior_land_use(res_defor, plfa_filtered, "Deforestation"),  get_results_prior_land_use(res_min, plfa_filtered, "Mining")) %>%  mutate(Metrics = "PLFA content")
print(estimates_df_plfa)
```

```{r}
all_results_df <- bind_rows(estimates_df_otu, estimates_df_chao1,  estimates_df_shannon,  estimates_df_simpson,  estimates_df_asco, estimates_df_basidio, estimates_df_beta,  estimates_df_comp,  estimates_df_plfa)
```

```{r}
all_results_df$Metrics <- factor(all_results_df$Metrics, levels = c("OTU richness", "Chao1 richness", "Shannon index", "Simpson index", "Ascomycota", "Basidiomycota", "Beta diversity", "Community structure", "PLFA content"))

prior_land_use_resvsdeg <- ggplot(all_results_df, aes(x = Estimate, y = Prior_land_use)) + geom_errorbar(aes(xmin = ci.lb, xmax = ci.ub), width = 0.2, alpha = 0.7) + geom_point(size = 2.5) + geom_vline(xintercept = 0, linetype = "dashed", color = "red") + facet_wrap(~ Metrics, scales = "free") + geom_text(aes(x = ci.lb, label = K), position = position_dodge(width = 0.5), hjust = 1.2, size = 3.2, show.legend = FALSE) + geom_text(aes(x = ci.ub, label = Percentage), position = position_dodge(width = 0.5), hjust = -0.2, size = 3.2, show.legend = FALSE) + labs(x = "lnRR", y = "") + theme_pubr(base_size = 12, border = TRUE) + theme(axis.text.y = element_text(size = 9), strip.text = element_text(face = "bold"), plot.title = element_text(hjust = 0.5, face = "bold")) + scale_x_continuous(expand = expansion(mult = c(0.4, 0.6)))
prior_land_use_resvsdeg
```

```{r eval=FALSE}
ggsave("../Figure_S4.jpg",  plot = prior_land_use_resvsdeg,  dpi = 800, height = 8, width = 11)
```

```{r}
sessionInfo()
```
